---
title: "Dictionary Analysis II"
subtitle: "analysis at politicians level" 
author: "Riccardo Ruta"
date: "5/2022"
output: 
  pdf_document:
    toc: yes
    latex_engine: xelatex
---

```{r setup2, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
source(here::here("src","00_setup.R"))
```

```{r}
# import dictionaries file
dict <-  read_excel("data/populism_dictionaries.xlsx")
variable.names(dict)

# create the dictionary
Rooduijn_Pauwels_Italian <-
  dictionary(list(populism =
                    (dict$Rooduijn_Pauwels_Italian
                     [!is.na(dict$Rooduijn_Pauwels_Italian)])))

Grundl_Italian_adapted <-
  dictionary(list(populism =
                    dict$Grundl_Italian_adapted
                  [!is.na(dict$Grundl_Italian_adapted)]))

Decadri_Boussalis <-
  dictionary(list(populism =
                    dict$Decadri_Boussalis
                  [!is.na(dict$Decadri_Boussalis)]))

Decadri_Boussalis_Grundl <-
  dictionary(list(people =
                    dict$Decadri_Boussalis_Grundl_People
                  [!is.na(dict$Decadri_Boussalis_Grundl_People)],
                  common_will =
                    dict$`Decadri_Boussalis_Grundl_Common Will`
                  [!is.na(dict$`Decadri_Boussalis_Grundl_Common Will`)],
                  elite =
                    dict$Decadri_Boussalis_Grundl_Elite
                  [!is.na(dict$Decadri_Boussalis_Grundl_Elite)]))
```

```{r}
dictionaries <- c("Rooduijn_Pauwels_Italian", "Grundl_Italian_adapted",
                  "Decadri_Boussalis","Decadri_Boussalis_Grundl")
n.words <- c(length(Rooduijn_Pauwels_Italian$populism),
           length(Grundl_Italian_adapted$populism),
           length(Decadri_Boussalis$populism),
           (length(Decadri_Boussalis_Grundl$people)+
              length(Decadri_Boussalis_Grundl$common_will)+
              length(Decadri_Boussalis_Grundl$elite))
            )
number_of_words <- data.frame(dictionaries,n.words)
kable(number_of_words)
```

```{r, include=FALSE}
load("data/dfm.Rda")
```

### Group and weight the dfm

```{r}
# By politician & month
dfm_weigh_name_month <- dfm_group(DFM, groups = interaction(nome, month)) %>% dfm_weight(scheme = "prop")
# By pol & quarter
dfm_weigh_name_quart <- dfm_group(DFM, groups = interaction(nome, quarter)) %>% dfm_weight(scheme = "prop")
# By pol & year
dfm_weigh_name_year <- dfm_group(DFM, groups = interaction(nome, year)) %>% dfm_weight(scheme = "prop")
# By pol & day
dfm_weigh_name_day <- dfm_group(DFM, groups = interaction(nome, date)) %>% dfm_weight(scheme = "prop")
```


\newpage

## Rooduijn_Pauwels_Italian

```{r}
# Dictionary analysis with Rooduijn_Pauwels_Italian
# By quarter
dfm_dict2_name  <- dfm_lookup(dfm_weigh_name_quart, dictionary = Rooduijn_Pauwels_Italian)
# Group by date
dfm_by_date2_name <- dfm_lookup(dfm_weigh_name_day, dictionary = Rooduijn_Pauwels_Italian)
```


### Most populist politician

```{r}
dict2_tstat_nome <- textstat_frequency(dfm_dict2_name, groups = nome)

kable(dict2_tstat_nome %>% slice_max(frequency, n = 20))
```
### Distribution of politician populism

```{r}
summary(dict2_tstat_nome$frequency)
#TBD
```


```{r}
# above the median
dict2_tstat_nome %>% filter(frequency > median(frequency)) %>% count()
# above the mean
dict2_tstat_nome %>% filter(frequency > mean(frequency)) %>% count()
# below the first quantiles
dict2_tstat_nome %>% filter(frequency < 0.18584 ) %>% count()
# above the third quantiles
dict2_tstat_nome %>% filter(frequency > 1.48826 ) %>% count()
```

\newpage





## Grundl_Italian_adapted

```{r, warning=FALSE}
# Dictionary analysis with Grundl_Italian_adapted
# By quarter
dfm_dict3_name <- dfm_lookup(dfm_weigh_name_quart, dictionary = Grundl_Italian_adapted)
# Group by date
dfm_by_date3_name <- dfm_lookup(dfm_weigh_name_day, dictionary = Grundl_Italian_adapted)
#dfm_by_date2
```




### Most populist politician

```{r}
dict_3_tstat_nome <- textstat_frequency(dfm_dict3_name, groups = nome)

kable(dict_3_tstat_nome %>% slice_max(frequency, n = 20))
```


### Distribution of politician populism

```{r}
# TBD
summary(dict_3_tstat_nome$frequency)

```




```{r}
# above the median
dict_3_tstat_nome %>% filter(frequency > median(frequency)) %>% count()
# above the mean
dict_3_tstat_nome %>% filter(frequency > mean(frequency)) %>% count()
# below the first quantiles
dict_3_tstat_nome %>% filter(frequency < 0.23802) %>% count()
# above the third quantiles
dict_3_tstat_nome %>% filter(frequency > 1.56229 ) %>% count()
```





## Decadri_Boussalis


```{r, warning=FALSE}
# Dictionary analysis with Decadri_Boussalis
# By quarter
dfm_dict4_name  <- dfm_lookup(dfm_weigh_name_quart, dictionary = Decadri_Boussalis)
# By date
dfm_by_date4_name <- dfm_lookup(dfm_weigh_name_day, dictionary = Decadri_Boussalis)

```




### Most populist politician

```{r}
dict_4_tstat_nome <- textstat_frequency(dfm_dict4_name, groups = nome)

kable(dict_4_tstat_nome %>% slice_max(frequency, n = 20))
```

### Distribution of politician populism

```{r}
#TBD
summary(dict_4_tstat_nome$frequency)
```

```{r}
# above the median
dict_4_tstat_nome %>% filter(frequency > median(frequency)) %>% count()
# above the mean
dict_4_tstat_nome %>% filter(frequency > mean(frequency)) %>% count()
# below the first quantiles
dict_4_tstat_nome %>% filter(frequency < 0.51949) %>% count()
# above the third quantiles
dict_4_tstat_nome %>% filter(frequency > 4.29796 ) %>% count()
```





## Compare how the dictionaries score for the most populist politician
**  DA AGGIUSTARE!!!**
```{r, eval=FALSE, include=FALSE}
# DA AGGIUSTARE!!!
top_20_nome_2 <- dict2_tstat_nome %>% arrange(desc(frequency)) %>% head(20)
top_20_nome_2$my_rank <- rank(top_20_nome_2$frequency)

top_20_nome_3 <- dict_3_tstat_nome %>% arrange(desc(frequency)) %>% head(20)
top_20_nome_3$my_rank <- rank(top_20_nome_3$frequency)

top_20_nome_4 <- dict_4_tstat_nome %>% arrange(desc(frequency)) %>% head(20)
top_20_nome_4$my_rank <- rank(top_20_nome_4$frequency)







# define the politicians list
pol <- unique(c(top_20_nome_4$group,top_20_nome_3$group,top_20_nome_2$group))

# create an empty df
pol_rank <- data.frame(first = vector(), second = vector(),
                         third = vector(), fourth = vector() )

# loop the rank for each pol
for (i in pol)
{
  rank_dict_pol_2 <- (top_20_nome_2 %>% if_else(group == i,
                                                .$my_rank,"na"))
  rank_dict_pol_3 <- (top_20_nome_3 %>% if_else(group == i,
                                                .$my_rank, "na"))
  rank_dict_pol_4 <- (top_20_nome_4 %>% if_else(group == i,
                                                .$my_rank, "na"))
  
  pol <- (i)
  pol_rank <- rbind(pol_rank, cbind(pol, rank_dict_pol_2,
                                        rank_dict_pol_3, rank_dict_pol_4))
}

# change the format of the columns in numeric
pol_rank$rank_dict_pol_2 <- as.numeric(pol_rank$rank_dict_pol_2)
pol_rank$rank_dict_pol_3 <- as.numeric(pol_rank$rank_dict_pol_3)
pol_rank$rank_dict_pol_4 <- as.numeric(pol_rank$rank_dict_pol_4)

# Create the column with the sum of the single score
pol_rank$total_score <- rowSums(pol_rank[,-1])
kable(pol_rank)
```












