---
title: "Dictionary Analysis"
author: "Riccardo Ruta"
date: "5/2022"
output: 
  pdf_document:
    toc: yes
    latex_engine: xelatex
---

```{r setup2, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
source(here::here("src","00_setup.R"))
```

# Dictionary analysis

At the level of political parties, which ones make most use of populist rhetoric?

At the level of individual politicians, which ones make most use of populist rhetoric?

I use 3 dictionary to perform the analysis

-   Rooduijn & Pauwels: Rooduijn, M., and T. Pauwels. 2011. "Measuring Populism: Comparing Two Methods of Content Analysis." West European Politics 34 (6): 1272--1283.

-   Decadri & Boussalis: Decadri, S., & Boussalis, C. (2020). Populism, party membership, and language complexity in the Italian chamber of deputies. Journal of Elections, Public Opinion and Parties, 30(4), 484-503.

-   Grundl: Gründl J. Populist ideas on social media: A dictionary-based measurement of populist communication. New Media & Society. December 2020.

-   Decadri & Boussalis + Grundl: this is simply a more extended version of the D&B dictionary, which also contains some terms taken from Grundl.

## Create the dictionary

I imported the excel file with the words for the dictionaries, excluding NA's.

```{r}
# import dictionaries file
dict <-  read_excel("data/populism_dictionaries.xlsx")
variable.names(dict)

# create the dictionary
Rooduijn_Pauwels_Italian <-
  dictionary(list(populism =
                    (dict$Rooduijn_Pauwels_Italian
                     [!is.na(dict$Rooduijn_Pauwels_Italian)])))

Grundl_Italian_adapted <-
  dictionary(list(populism =
                    dict$Grundl_Italian_adapted
                  [!is.na(dict$Grundl_Italian_adapted)]))

Decadri_Boussalis <-
  dictionary(list(populism =
                    dict$Decadri_Boussalis
                  [!is.na(dict$Decadri_Boussalis)]))

Decadri_Boussalis_Grundl <-
  dictionary(list(people =
                    dict$Decadri_Boussalis_Grundl_People
                  [!is.na(dict$Decadri_Boussalis_Grundl_People)],
                  common_will =
                    dict$`Decadri_Boussalis_Grundl_Common Will`
                  [!is.na(dict$`Decadri_Boussalis_Grundl_Common Will`)],
                  elite =
                    dict$Decadri_Boussalis_Grundl_Elite
                  [!is.na(dict$Decadri_Boussalis_Grundl_Elite)]))
```

```{r}
dictionaries <- c("Rooduijn_Pauwels_Italian", "Grundl_Italian_adapted",
                  "Decadri_Boussalis","Decadri_Boussalis_Grundl")
n.words <- c(length(Rooduijn_Pauwels_Italian$populism),
           length(Grundl_Italian_adapted$populism),
           length(Decadri_Boussalis$populism),
           (length(Decadri_Boussalis_Grundl$people)+
              length(Decadri_Boussalis_Grundl$common_will)+
              length(Decadri_Boussalis_Grundl$elite))
            )
number_of_words <- data.frame(dictionaries,n.words)
kable(number_of_words)
```

```{r, include=FALSE}
load("data/dfm.Rda")
```

### Group and weight the dfm

```{r}
# By party & month
dfm_weigh_p_month <- dfm_group(DFM, groups = interaction(party_id, month)) %>% dfm_weight(scheme = "prop")
# By party & quarter
dfm_weigh_p_quart <- dfm_group(DFM, groups = interaction(party_id, quarter)) %>% dfm_weight(scheme = "prop")
# By party & year
dfm_weigh_p_year <- dfm_group(DFM, groups = interaction(party_id, year)) %>% dfm_weight(scheme = "prop")
# By party & day
dfm_weigh_p_day <- dfm_group(DFM, groups = interaction(party_id, date)) %>% dfm_weight(scheme = "prop")

```



\newpage

**Apply dictionary**

## Decadri_Boussalis_Grundl

### Level of sparsity

daily: 12.08%

weekly: 0.55%

monthly: 0%

```{r, warning=FALSE}
# Dictionary analysis with Decadri_Boussalis_Grundl
# By quarter
dfm_dict1  <- dfm_lookup(dfm_weigh_p_quart, dictionary = Decadri_Boussalis_Grundl)
# By date
dfm_by_date1 <- dfm_lookup(dfm_weigh_p_day, dictionary = Decadri_Boussalis_Grundl)

```

```{r, echo=FALSE}
tstat1 <- textstat_frequency(dfm_dict1, groups = party_id)

ggplot(data = tstat1, aes(x = factor(nrow(tstat1):1), y = frequency)) +
    geom_point() +
    facet_wrap(~ group, scales = "free") +
    coord_flip() +
    scale_x_discrete(breaks = nrow(tstat1):1,
                       labels = tstat1$feature) +
    labs(x = NULL, y = "Relative frequency")
```

Looking at the populist rhetoric for each party divided into the 3 components people-centrism, anti-elitism and common-will, we note that the most frequent components is People-centrism.

### General level of populism in time divided into 3 components

```{r}
dat_smooth1.1 <- ksmooth(x = dfm_by_date1$date, 
                      y = dfm_by_date1[,"people"] - !dfm_by_date1[,"people"],
                      kernel = "normal", bandwidth = 30)

dat_smooth1.2 <- ksmooth(x = dfm_by_date1$date, 
                      y = dfm_by_date1[,"common_will"] - !dfm_by_date1[,"common_will"],
                      kernel = "normal", bandwidth = 30)

dat_smooth1.3 <- ksmooth(x = dfm_by_date1$date, 
                      y = dfm_by_date1[,"elite"] - !dfm_by_date1[,"elite"],
                      kernel = "normal", bandwidth = 30)

plot_time_1 <- plot(dat_smooth1.1$x, dat_smooth1.1$y,
                    type = "l", ylab = "Populism level", xlab = "Time",  ylim = c(-1,0), xlim = c(min(dfm_by_date1$date),max(dfm_by_date1$date)))
  
  lines(dat_smooth1.2$x, dat_smooth1.2$y,
        type = "l", ylab = "Populism level", xlab = "Time",col = "blue") 
  
  lines(dat_smooth1.3$x, dat_smooth1.3$y,
        type = "l", ylab = "Populism level", xlab = "Time", col = "green") 
  
  legend("topleft", legend = c("people","elite","common_will"),
         fill = c("black", "green", "blue"))
  axis(1, dfm_by_date1$date,
     format(dfm_by_date1$date, "%y-%m"))
  grid()
  title(main = "General level of populism divided into 3 components")
  

```

This plot is coherent with the previous one and show us that people is the Component that score better.

### General level of populism in time

```{r}
dat_smooth1 <- ksmooth(x = dfm_by_date1$date, 
                       y = ((dfm_by_date1[,"people"]+
                              dfm_by_date1[,"common_will"]+
                              dfm_by_date1[,"elite"])/3) -
                         !((dfm_by_date1[,"people"]+
                              dfm_by_date1[,"common_will"]+
                              dfm_by_date1[,"elite"])/3),
                       kernel = "normal", bandwidth = 30)

plot_time_1 <- plot(dat_smooth1$x, dat_smooth1$y,
                    type = "l", ylab = "Populism level", xlab = "Time")
                    axis(1, dat_smooth1$x,
                         format(dat_smooth1$x, "%y-%m"))
                    grid()
title(main = "General level of populism with Decadri_Boussalis_Grundl dictionary")
```
### Most populist parliamentary group for each component

```{r}
# Most populist parliamentary group
dfm_dict1_tstat_party <- textstat_frequency(dfm_dict1, groups = party_id)
kable(dfm_dict1_tstat_party %>% filter(feature == "people") %>% slice_max(frequency, n = 20))
kable(dfm_dict1_tstat_party %>% filter(feature == "elite") %>% slice_max(frequency, n = 20))
kable(dfm_dict1_tstat_party %>% filter(feature == "common_will") %>% slice_max(frequency, n = 20))
```
### Most populist parliamentary group

```{r}
# Add variable for the general level of populism
dfm_dict1_tstat_party <- dfm_dict1_tstat_party %>%
  group_by(group) %>% mutate(populism = mean(frequency))
dfm_dict1_tstat_party_filtered <- dfm_dict1_tstat_party %>%
  select(group,populism) %>% unique() %>% arrange(desc(populism))
kable(dfm_dict1_tstat_party_filtered)
```



\newpage

## Rooduijn_Pauwels_Italian

### Level of sparsity

daily: 0.60%

weekly: 0.%

monthly: 0%

```{r, warning=FALSE}
# Dictionary analysis with Rooduijn_Pauwels_Italian
# By quarter
dfm_dict2  <- dfm_lookup(dfm_weigh_p_quart, dictionary = Rooduijn_Pauwels_Italian)
# Group by date
dfm_by_date2 <- dfm_lookup(dfm_weigh_p_day, dictionary = Rooduijn_Pauwels_Italian)
#dfm_by_date2

# Group by week
#dfm_by_week2 <- dfm_group(dfm_dict2, groups= week)
#dfm_by_week2
# Group by month
#dfm_by_month2 <- dfm_group(dfm_dict2, groups= month)

#kable(dfm_by_month2)
```

### General level of populism in time

```{r, echo=FALSE}
dat_smooth2 <- ksmooth(x = dfm_by_date2$date, 
                      y = dfm_by_date2[,"populism"] - !dfm_by_date2[,"populism"],
                      kernel = "normal", bandwidth = 30)

plot_time_2 <- plot(dat_smooth2$x, dat_smooth2$y, type = "l", ylab = "Populism level", xlab = "Time") + 
  abline(h = 0, lty = 2)
grid()
title(main = "General level of populism with Rooduijn_Pauwels_Italian dictionary")

```

### Most populist parliamentary group

```{r}
# Most populist parliamentary group
dfm_dict2_tstat_party <- textstat_frequency(dfm_dict2, groups = party_id)
kable(dfm_dict2_tstat_party %>% slice_max(frequency, n = 20))
```

### Distribution of parliamentary group populism

```{r, eval=T}
summary(dfm_dict2_tstat_party$frequency)
```

```{r, eval=FALSE}
#TBD
hist(dfm_dict2_tstat_party$frequency, prob=T)
points(density(dfm_dict2_tstat_party$frequency),type="l",col="blue")
rug(dfm_dict2_tstat_party$frequency,col="red")

m <- mean(dfm_dict2_tstat_party$frequency)
std<-sqrt(var(dfm_dict2_tstat_party$frequency))

hist(dfm_dict2_tstat_party$frequency,prob=T,main="Frequency")

curve(dnorm(x, mean=m, sd=std), col="darkblue", lwd=2, add=TRUE)

```

```{r}
# above the median
kable(dfm_dict2_tstat_party  %>% filter(frequency > median(frequency)))
# above the mean
kable(dfm_dict2_tstat_party %>% filter(frequency > mean(frequency)))
# below the first quantiles
kable(dfm_dict2_tstat_party %>% filter(frequency < 0.0070015))
# above the third quantiles
kable(dfm_dict2_tstat_party %>% filter(frequency > 0.0158277))
```






\newpage

## Grundl_Italian_adapted

### Level of sparsity

daily: 0.24%

weekly: 0.0%

monthly: 0%

```{r, warning=FALSE}
# Dictionary analysis with Grundl_Italian_adapted
# By quarter
dfm_dict3  <- dfm_lookup(dfm_weigh_p_quart, dictionary = Grundl_Italian_adapted)
# Group by date
dfm_by_date3 <- dfm_lookup(dfm_weigh_p_day, dictionary = Grundl_Italian_adapted)
#dfm_by_date2
```

### General level of populism in time

```{r, echo=FALSE}
dat_smooth3 <- ksmooth(x = dfm_by_date3$date, 
                      y = dfm_by_date3[,"populism"] - !dfm_by_date3[,"populism"],
                      kernel = "normal", bandwidth = 30)
plot_time_3 <- plot(dat_smooth3$x, dat_smooth3$y, type = "l", ylab = "Populism level", xlab = "Time") +
  abline(h = 0, lty = 2)
grid()
title(main = "General level of populism with Grundl_Italian_adapted dictionary")

```

### Most populist parliamentary group

```{r}
# Most populist parliamentary group
dict_3_tstat_party <- textstat_frequency(dfm_dict3, groups = party_id)

kable(dict_3_tstat_party %>% slice_max(frequency, n = 20))
```

### Distribution of parliamentary grouppopulism

```{r}
#TBD
summary(dict_3_tstat_party$frequency)
```
```{r}
# above the median
kable(dict_3_tstat_party  %>% filter(frequency > median(frequency)))
# above the mean
kable(dict_3_tstat_party %>% filter(frequency > mean(frequency)))
# below the first quantiles
kable(dict_3_tstat_party %>% filter(frequency < 0.013448))
# above the third quantiles
kable(dict_3_tstat_party %>% filter(frequency > 0.022582 ))
```





\newpage

## Decadri_Boussalis

### Level of sparsity

daily: 0%

weekly: 0.0%

monthly: 0%

```{r, warning=FALSE}
# Dictionary analysis with Decadri_Boussalis
# By quarter
dfm_dict4  <- dfm_lookup(dfm_weigh_p_quart, dictionary = Decadri_Boussalis)
# By date
dfm_by_date4 <- dfm_lookup(dfm_weigh_p_day, dictionary = Decadri_Boussalis)

```

### General level of populism in time

```{r, echo=FALSE}
dat_smooth4 <- ksmooth(x = dfm_by_date4$date, 
                      y = dfm_by_date4[,"populism"] - !dfm_by_date4[,"populism"],
                      kernel = "normal", bandwidth = 30)
plot_time_4 <- plot(dat_smooth4$x, dat_smooth4$y, type = "l", ylab = "Populism level", xlab = "Time") +
  abline(h = 0, lty = 2)+
  points(x = 2021-11-05, y = 4,type="p", pch=21, col="black", bg=NA, cex=1)
grid()
title(main = "General level of populism with Decadri_Boussalis dictionary")
```

### Most populist parliamentary group

```{r}
# Most populist parliamentary group
dict_4_tstat_party <- textstat_frequency(dfm_dict4, groups = party_id)

kable(dict_4_tstat_party %>% slice_max(frequency, n = 20))
```

### Distribution of party populism

```{r}
#TBD
summary(dict_4_tstat_party$frequency)

```

```{r}
# above the median
kable(dict_4_tstat_party  %>% filter(frequency > median(frequency)))
# above the mean
kable(dict_4_tstat_party %>% filter(frequency > mean(frequency)))
# below the first quantiles
kable(dict_4_tstat_party %>% filter(frequency < 0.04892 ))
# above the third quantiles
kable(dict_4_tstat_party %>% filter(frequency > 0.06287  ))
```


## Compare the general level of populism in time for the dictionaries

```{r, echo=FALSE, warning=FALSE}
comparison_time <- plot(dat_smooth4$x, dat_smooth4$y,
                        type = "l", ylab = "Populism level", xlab = "Time", col = "green", ylim = c(-0.7,-0.1))+
  lines(dat_smooth3$x, dat_smooth3$y,
        type = "l", ylab = "Populism level", xlab = "Time", col = "blue")+
  lines(dat_smooth2$x, dat_smooth2$y,
        type = "l", ylab = "Populism level", xlab = "Time", col = "red") +
  lines(dat_smooth1$x, dat_smooth1$y,
        type = "l", ylab = "Populism level", xlab = "Time", col = "black")
legend("topleft", legend = c("Roodujin_pauwels","Grundl_italian",
                             "Decadri_Boussalis", "Decadri_Boussalis_Grundl"),
       fill = c("red", "blue", "green", "Black"))
grid()
title(main = "Compare how the different dictionaries score")
```


## Compare how the dictionaries score for the most populist parliamentary group

```{r}
# Create the columns with the "populist score"
# 11 for the "most populist" and 1 for the least
dfm_dict1_tstat_party_filtered$my_rank <- rank(dfm_dict1_tstat_party_filtered$populism)
dfm_dict2_tstat_party$my_rank <- rank(dfm_dict2_tstat_party$frequency)
dict_3_tstat_party$my_rank <- rank(dict_3_tstat_party$frequency)
dict_4_tstat_party$my_rank <- rank(dict_4_tstat_party$frequency)

# define the parliamentary group list
party <- c("LEGA","PD","M5S","FI","FDI","MISTO",
           "LEU","CI","IV","INDIPENDENTE","REG_LEAGUES")
# create an empty df
party_rank <- data.frame(first = vector(), second = vector(),
                         third = vector(), fourth = vector(), fifth = vector() )

# loop the rank for each parliamentary group
for (i in party)
{
  rank_dict_1 <- (dfm_dict1_tstat_party_filtered %>% filter(group == i ) %>% .$my_rank)
  rank_dict_2 <- (dfm_dict2_tstat_party %>% filter(group == i ) %>% .$my_rank)
  rank_dict_3 <- (dict_3_tstat_party %>% filter(group == i ) %>% .$my_rank)
  rank_dict_4 <- (dict_4_tstat_party %>% filter(group == i ) %>% .$my_rank)
  
  party <- (i)
  party_rank <- rbind(party_rank, cbind(party, rank_dict_1, rank_dict_2,
                                        rank_dict_3, rank_dict_4))
}

# change the format of the columns in numeric
party_rank$rank_dict_1 <- as.numeric(party_rank$rank_dict_1)
party_rank$rank_dict_2 <- as.numeric(party_rank$rank_dict_2)
party_rank$rank_dict_3 <- as.numeric(party_rank$rank_dict_3)
party_rank$rank_dict_4 <- as.numeric(party_rank$rank_dict_4)

# Create the column with the sum of the single score
party_rank$total_score <- rowSums(party_rank[,-1])
kable(party_rank %>% arrange(desc(total_score)))
```




























