---
title: "Dictionary Analysis"
author: "Riccardo Ruta"
date: "5/2022"
output: 
  pdf_document:
    toc: yes
    latex_engine: xelatex
---

```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
source(here::here("src","00_setup.R"))
```

### RICORSO ALLA RETORICA POPULISTA.

### At the level of political parties, which ones make most use of populist rhetoric?

### At the level of individual politicians, which ones make most use of populist rhetoric?

-   Rooduijn & Pauwels: Rooduijn, M., and T. Pauwels. 2011. "Measuring Populism: Comparing Two Methods of Content Analysis." West European Politics 34 (6): 1272--1283.

-   Decadri & Boussalis: Decadri, S., & Boussalis, C. (2020). Populism, party membership, and language complexity in the Italian chamber of deputies. Journal of Elections, Public Opinion and Parties, 30(4), 484-503.

-   Grundl: Gründl J. Populist ideas on social media: A dictionary-based measurement of populist communication. New Media & Society. December 2020.

-   Decadri & Boussalis + Grundl: this is simply a more extended version of the D&B dictionary, which also contains some terms taken from Grundl.

# 1) First step, import the words and create the dictionary

```{r}
# import dictionaries file
dict <-  read_excel("data/populism_dictionaries.xlsx")
variable.names(dict)

# create the dictionary
Rooduijn_Pauwels_Italian <-
  dictionary(list(populism =
                    (dict$Rooduijn_Pauwels_Italian
                     [!is.na(dict$Rooduijn_Pauwels_Italian)])))

Grundl_Italian_adapted <-
  dictionary(list(populism =
                    dict$Grundl_Italian_adapted
                  [!is.na(dict$Grundl_Italian_adapted)]))

Decadri_Boussalis <-
  dictionary(list(populism =
                    dict$Decadri_Boussalis
                  [!is.na(dict$Decadri_Boussalis)]))

Decadri_Boussalis_Grundl <-
  dictionary(list(people =
                    dict$Decadri_Boussalis_Grundl_People
                  [!is.na(dict$Decadri_Boussalis_Grundl_People)],
                  common_will =
                    dict$`Decadri_Boussalis_Grundl_Common Will`
                  [!is.na(dict$`Decadri_Boussalis_Grundl_Common Will`)],
                  elite =
                    dict$Decadri_Boussalis_Grundl_Elite
                  [!is.na(dict$Decadri_Boussalis_Grundl_Elite)]))


```


# 2) Import the DFM prepared in previous steps and apply dictionaries

```{r, include=FALSE}
load("data/dfm_weight.Rda")
```

# I) Decadri_Boussalis_Grundl

### Level of sparsity

daily: 12.08%

weekly: 0.55%

monthly: 0%

```{r, warning=FALSE}
# Daily Dictionary analysis with Decadri_Boussalis_Grundl on the whole dataset
dfm_dict1  <- dfm_lookup(dfm_weight, dictionary = Decadri_Boussalis_Grundl)
# Group by date
dfm_by_date1 <- dfm_group(dfm_dict1, groups= date)
dfm_by_date1
# Group by week
dfm_by_week1 <- dfm_group(dfm_dict1, groups= week)
dfm_by_week1
# Group by month
dfm_by_month1 <- dfm_group(dfm_dict1, groups= month)
dfm_by_month1
```



```{r, echo=FALSE}
tstat1 <- textstat_frequency(dfm_dict1, groups = party_id)

ggplot(data = tstat1, aes(x = factor(nrow(tstat1):1), y = frequency)) +
    geom_point() +
    facet_wrap(~ group, scales = "free") +
    coord_flip() +
    scale_x_discrete(breaks = nrow(tstat1):1,
                       labels = tstat1$feature) +
    labs(x = NULL, y = "Relative frequency")
```

Looking at the populist rhetoric for each party divided into the 3 components people-centrism, anti-elitism and common-will, we note that the most frequent components is People-centrism.

# II) Rooduijn_Pauwels_Italian
### Level of sparsity

daily: 0.60%

weekly: 0.%

monthly: 0%

```{r, warning=FALSE}
# Daily Dictionary analysis with Rooduijn_Pauwels_Italian on the whole dataset
dfm_dict2  <- dfm_lookup(dfm_weight, dictionary = Rooduijn_Pauwels_Italian)
# Group by date
dfm_by_date2 <- dfm_group(dfm_dict2, groups= date)
dfm_by_date2
# Group by week
dfm_by_week2 <- dfm_group(dfm_dict2, groups= week)
dfm_by_week2
# Group by month
dfm_by_month2 <- dfm_group(dfm_dict2, groups= month)
dfm_by_month2
```

## General level of populism in time

```{r, echo=FALSE}
dat_smooth2 <- ksmooth(x = dfm_by_date2$date, 
                      y = dfm_by_date2[,"populism"] - !dfm_by_date2[,"populism"],
                      kernel = "normal", bandwidth = 30)
plot_time_2 <- plot(dat_smooth2$x, dat_smooth2$y, type = "l", ylab = "Populism level", xlab = "Time") + 
  abline(h = 0, lty = 2)

```

## Most populist party

```{r}
# Most populist party
dfm_dict2_tstat_party <- textstat_frequency(dfm_dict2, groups = party_id)
kable(dfm_dict2_tstat_party %>% slice_max(frequency, n = 20))
```

## Most populist politician

```{r}
dict2_tstat_nome <- textstat_frequency(dfm_dict2, groups = nome)

kable(dict2_tstat_nome %>% slice_max(frequency, n = 20))
```







# III) Grundl_Italian_adapted

### Level of sparsity

daily: 0.24%

weekly: 0.0%

monthly: 0%

```{r, warning=FALSE}
# Daily Dictionary analysis with Grundl_Italian_adapted on the whole dataset
dfm_dict3  <- dfm_lookup(dfm_weight, dictionary = Grundl_Italian_adapted)
# Group by date
dfm_by_date3<- dfm_group(dfm_dict3, groups= date)
dfm_by_date3
# Group by week
dfm_by_week3 <- dfm_group(dfm_dict3, groups= week)
dfm_by_week3
# Group by month
dfm_by_month3 <- dfm_group(dfm_dict3, groups= month)
dfm_by_month3
```


## General level of populism in time

```{r, echo=FALSE}
dat_smooth3 <- ksmooth(x = dfm_by_date3$date, 
                      y = dfm_by_date3[,"populism"] - !dfm_by_date3[,"populism"],
                      kernel = "normal", bandwidth = 30)
plot_time_3 <- plot(dat_smooth3$x, dat_smooth3$y, type = "l", ylab = "Populism level", xlab = "Time") +
  abline(h = 0, lty = 2)

```


## Most populist party

```{r}
# Most populist party
dict_3_tstat_party <- textstat_frequency(dfm_dict3, groups = party_id)
kable(dict_3_tstat_party %>% slice_max(frequency, n = 20))
```

## Most populist politician

```{r}
dict_3_tstat_nome <- textstat_frequency(dfm_dict3, groups = nome)

kable(dict_3_tstat_nome %>% slice_max(frequency, n = 20))
```








# IV) Decadri_Boussalis

### Level of sparsity

daily: 0%

weekly: 0.0%

monthly: 0%

```{r, warning=FALSE}
# Daily Dictionary analysis with Decadri_Boussalis on the whole dataset
dfm_dict4  <- dfm_lookup(dfm_weight, dictionary = Decadri_Boussalis)
# Group by date
dfm_by_date4<- dfm_group(dfm_dict4, groups= date)
dfm_by_date4
# Group by week
dfm_by_week4 <- dfm_group(dfm_dict4, groups= week)
dfm_by_week4
# Group by month
dfm_by_month4 <- dfm_group(dfm_dict4, groups= month)
dfm_by_month4
```

## General level of populism in time

```{r, echo=FALSE}
dat_smooth4 <- ksmooth(x = dfm_by_date4$date, 
                      y = dfm_by_date4[,"populism"] - !dfm_by_date4[,"populism"],
                      kernel = "normal", bandwidth = 30)
plot_time_4 <- plot(dat_smooth4$x, dat_smooth4$y, type = "l", ylab = "Populism level", xlab = "Time") +
  abline(h = 0, lty = 2)
```


## Most populist party

```{r}
# Most populist party
dict_4_tstat_party <- textstat_frequency(dfm_dict4, groups = party_id)
kable(dict_4_tstat_party %>% slice_max(frequency, n = 20))
```

## Most populist politician

```{r}
dict_4_tstat_nome <- textstat_frequency(dfm_dict4, groups = nome)

kable(dict_4_tstat_nome %>% slice_max(frequency, n = 20))
```





```{r}
# TEST
ggplot(dict_4_tstat_nome, aes(x=frequency)) +
  geom_histogram(binwidth=.5, colour="black", fill="white") +
    geom_vline(aes(xintercept=mean(frequency, na.rm=T)),   # Ignore NA values for mean
               color="red", linetype="dashed", size=1)
```

