---
title: "Sentiment Analysis"
subtitle: "Analysis performed using Syuzhet Packages (www.rdocumentation.org/packages/syuzhet/versions/1.0.6)"
author: "Riccardo Ruta"
date: "5/2022"
output: 
  pdf_document:
    toc: yes
    latex_engine: xelatex
---

```{r setup3, include=FALSE}
 knitr::opts_chunk$set(echo = FALSE)
source(here::here("src","00_setup.R"))
```

```{r, include=FALSE}
# load("data/dfm_trimmed.Rda")
load("data/dataset.Rda")
```

# Sentiment analysis
<http://saifmohammad.com/WebPages/lexicons.html>

## Inspect the dictionary

```{r, echo=TRUE}
head(get_sentiment_dictionary(dictionary = "nrc", language = "italian"),15)
```

### Clean text from dataframe 
Define function to make the text extracted from dataframe suitable for analysis

```{r, echo=TRUE}
# Define function to make the text suitable for analysis
clean.text = function(x)
{
  # tolower
  x = tolower(x)
  # remove rt
  x = gsub("rt", "", x)
  # remove at
  x = gsub("@\\w+", "", x)
  # remove punctuation
  x = gsub("[[:punct:]]", "", x)
  # remove numbers
  x = gsub("[[:digit:]]", "", x)
  # remove links http
  x = gsub("http\\w+", "", x)
  # remove tabs
  x = gsub("[ |\t]{2,}", "", x)
  # remove blank spaces at the beginning
  x = gsub("^ ", "", x)
  # remove blank spaces at the end
  x = gsub(" $", "", x)
  return(x)
}
```


## Create the filtered dataframes

```{r, echo=TRUE}
# Create filtered dataframes
MELONI <- dataset %>% filter(nome  == "MELONI Giorgia")
CONTE <- dataset %>% filter(nome  == "CONTE Giuseppe")
RENZI <- dataset %>% filter(nome  == "RENZI Matteo")
SALVINI <- dataset %>% filter(nome  == "SALVINI Matteo")
LETTA <- dataset %>% filter(nome  == "LETTA Enrico")
BERLUSCONI <- dataset %>% filter(nome  == "BERLUSCONI Silvio")
SPERANZA <- dataset %>% filter(nome  == "SPERANZA Roberto")
```

## Create nrc objects
```{r, eval=F, echo=TRUE}
# Create the nrc object
nrc_meloni <- get_nrc_sentiment(MELONI$tweet_testo, language="italian")
save(nrc_meloni,file="data/nrc_meloni.Rda")

nrc_conte <- get_nrc_sentiment(CONTE$tweet_testo, language="italian")
save(nrc_conte,file="data/nrc_conte.Rda")

nrc_renzi <- get_nrc_sentiment(RENZI$tweet_testo, language="italian")
save(nrc_renzi,file="data/nrc_renzi.Rda")

nrc_salvini <- get_nrc_sentiment(SALVINI$tweet_testo, language="italian")
save(nrc_salvini,file="data/nrc_salvini.Rda")

nrc_letta <- get_nrc_sentiment(LETTA$tweet_testo, language="italian")
save(nrc_letta,file="data/nrc_letta.Rda")

nrc_berlusconi <- get_nrc_sentiment(BERLUSCONI$tweet_testo, language="italian")
save(nrc_berlusconi, file="data/nrc_berlusconi.Rda")

nrc_speranza <- get_nrc_sentiment(SPERANZA$tweet_testo, language="italian")
save(nrc_speranza,file="data/nrc_speranza.Rda")
```

```{r, include=FALSE}
# load nrc object
load("data/nrc_meloni.Rda")
load("data/nrc_conte.Rda")
load("data/nrc_renzi.Rda")
load("data/nrc_salvini.Rda")
load("data/nrc_letta.Rda")
load("data/nrc_berlusconi.Rda")
load("data/nrc_speranza.Rda")
```

\newpage

## Giorgia Meloni
### Proportion of the emotion

```{r}
barplot(
  sort(colSums(prop.table(nrc_meloni[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Giorgia Meloni", xlab="Percentage"
)
```

### Wordcloud of emotions

```{r, warning=FALSE,  echo=FALSE}
all <- c(
  paste(MELONI$tweet_testo[nrc_meloni$anger > 0], collapse=" "),
  paste(MELONI$tweet_testo[nrc_meloni$anticipation > 0], collapse=" "),
  paste(MELONI$tweet_testo[nrc_meloni$disgust > 0], collapse=" "),
  paste(MELONI$tweet_testo[nrc_meloni$fear > 0], collapse=" "),
  paste(MELONI$tweet_testo[nrc_meloni$joy > 0], collapse=" "),
  paste(MELONI$tweet_testo[nrc_meloni$sadness > 0], collapse=" "),
  paste(MELONI$tweet_testo[nrc_meloni$surprise > 0], collapse=" "),
  paste(MELONI$tweet_testo[nrc_meloni$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear',
                   'joy', 'sadness', 'surprise', 'trust')
# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Giorgia Meloni')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099",
                            "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage


## Giuseppe Conte
### Proportion of the emotion
```{r}
barplot(
  sort(colSums(prop.table(nrc_conte[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Giuseppe Conte", xlab="Percentage"
)
```

### Wordcloud of emotions

```{r, warning=FALSE, echo=FALSE}
all <- c(
  paste(CONTE$tweet_testo[nrc_conte$anger > 0], collapse=" "),
  paste(CONTE$tweet_testo[nrc_conte$anticipation > 0], collapse=" "),
  paste(CONTE$tweet_testo[nrc_conte$disgust > 0], collapse=" "),
  paste(CONTE$tweet_testo[nrc_conte$fear > 0], collapse=" "),
  paste(CONTE$tweet_testo[nrc_conte$joy > 0], collapse=" "),
  paste(CONTE$tweet_testo[nrc_conte$sadness > 0], collapse=" "),
  paste(CONTE$tweet_testo[nrc_conte$surprise > 0], collapse=" "),
  paste(CONTE$tweet_testo[nrc_conte$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear', 'joy',
                   'sadness', 'surprise', 'trust')
# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Giuseppe Conte')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099",
                            "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage

## Matteo Renzi
### Proportion of the emotion

```{r}
barplot(
  sort(colSums(prop.table(nrc_renzi[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Matteo Renzi", xlab="Percentage"
)
```

### Wordcloud of emotions

```{r, warning=FALSE, echo=FALSE}
all <- c(
  paste(RENZI$tweet_testo[nrc_renzi$anger > 0], collapse=" "),
  paste(RENZI$tweet_testo[nrc_renzi$anticipation > 0], collapse=" "),
  paste(RENZI$tweet_testo[nrc_renzi$disgust > 0], collapse=" "),
  paste(RENZI$tweet_testo[nrc_renzi$fear > 0], collapse=" "),
  paste(RENZI$tweet_testo[nrc_renzi$joy > 0], collapse=" "),
  paste(RENZI$tweet_testo[nrc_renzi$sadness > 0], collapse=" "),
  paste(RENZI$tweet_testo[nrc_renzi$surprise > 0], collapse=" "),
  paste(RENZI$tweet_testo[nrc_renzi$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear',
                   'joy', 'sadness', 'surprise', 'trust')
# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Matteo Renzi')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099",
                            "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage

## Matteo Salvini

### Proportion of the emotion

```{r}
barplot(
  sort(colSums(prop.table(nrc_salvini[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Matteo Salvini", xlab="Percentage"
)
```

### Wordcloud of emotions

```{r, warning=FALSE}
all <- c(
  paste(SALVINI$tweet_testo[nrc_salvini$anger > 0], collapse=" "),
  paste(SALVINI$tweet_testo[nrc_salvini$anticipation > 0], collapse=" "),
  paste(SALVINI$tweet_testo[nrc_salvini$disgust > 0], collapse=" "),
  paste(SALVINI$tweet_testo[nrc_salvini$fear > 0], collapse=" "),
  paste(SALVINI$tweet_testo[nrc_salvini$joy > 0], collapse=" "),
  paste(SALVINI$tweet_testo[nrc_salvini$sadness > 0], collapse=" "),
  paste(SALVINI$tweet_testo[nrc_salvini$surprise > 0], collapse=" "),
  paste(SALVINI$tweet_testo[nrc_salvini$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear',
                   'joy', 'sadness', 'surprise', 'trust')
# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Matteo Salvini')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099",
                            "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage

## Enrico Letta

### Proportion of the emotion
```{r}
barplot(
  sort(colSums(prop.table(nrc_letta[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Enrico Letta", xlab="Percentage"
)
```

### Wordcloud of emotions
```{r, warning=FALSE}
all <- c(
  paste(LETTA$tweet_testo[nrc_letta$anger > 0], collapse=" "),
  paste(LETTA$tweet_testo[nrc_letta$anticipation > 0], collapse=" "),
  paste(LETTA$tweet_testo[nrc_letta$disgust > 0], collapse=" "),
  paste(LETTA$tweet_testo[nrc_letta$fear > 0], collapse=" "),
  paste(LETTA$tweet_testo[nrc_letta$joy > 0], collapse=" "),
  paste(LETTA$tweet_testo[nrc_letta$sadness > 0], collapse=" "),
  paste(LETTA$tweet_testo[nrc_letta$surprise > 0], collapse=" "),
  paste(LETTA$tweet_testo[nrc_letta$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear', 'joy', 'sadness', 'surprise', 'trust')
# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Enrico Letta')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099", "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage

## Silvio Berlusconi

### Proportion of the emotion
```{r}
barplot(
  sort(colSums(prop.table(nrc_berlusconi[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Silvio Berlusconi", xlab="Percentage"
)
```

### Wordcloud of emotions
```{r, warning=FALSE}
all <- c(
  paste(BERLUSCONI$tweet_testo[nrc_berlusconi$anger > 0], collapse=" "),
  paste(BERLUSCONI$tweet_testo[nrc_berlusconi$anticipation > 0], collapse=" "),
  paste(BERLUSCONI$tweet_testo[nrc_berlusconi$disgust > 0], collapse=" "),
  paste(BERLUSCONI$tweet_testo[nrc_berlusconi$fear > 0], collapse=" "),
  paste(BERLUSCONI$tweet_testo[nrc_berlusconi$joy > 0], collapse=" "),
  paste(BERLUSCONI$tweet_testo[nrc_berlusconi$sadness > 0], collapse=" "),
  paste(BERLUSCONI$tweet_testo[nrc_berlusconi$surprise > 0], collapse=" "),
  paste(BERLUSCONI$tweet_testo[nrc_berlusconi$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear',
                   'joy', 'sadness', 'surprise', 'trust')
# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Silvio Berlusconi')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099",
                            "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage

## Roberto Speranza

### Proportion of the emotion
```{r}
barplot(
  sort(colSums(prop.table(nrc_speranza[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Roberto Speranza", xlab="Percentage"
)
```

### Wordcloud of emotions
```{r, warning=FALSE}
all <- c(
  paste(SPERANZA$tweet_testo[nrc_speranza$anger > 0], collapse=" "),
  paste(SPERANZA$tweet_testo[nrc_speranza$anticipation > 0], collapse=" "),
  paste(SPERANZA$tweet_testo[nrc_speranza$disgust > 0], collapse=" "),
  paste(SPERANZA$tweet_testo[nrc_speranza$fear > 0], collapse=" "),
  paste(SPERANZA$tweet_testo[nrc_speranza$joy > 0], collapse=" "),
  paste(SPERANZA$tweet_testo[nrc_speranza$sadness > 0], collapse=" "),
  paste(SPERANZA$tweet_testo[nrc_speranza$surprise > 0], collapse=" "),
  paste(SPERANZA$tweet_testo[nrc_speranza$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear', 'joy', 'sadness', 'surprise', 'trust')

# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Roberto Speranza')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099", "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```
