---
title: "Emotion Analysis"
subtitle: "Analysis performed using Italian_LIWC2007 Dictionary"
author: "Riccardo Ruta"
date: "5/2022"
output: 
  pdf_document:
    toc: yes
    latex_engine: xelatex
---

```{r setup3, include=FALSE}
 knitr::opts_chunk$set(echo = T)
source(here::here("src","00_setup.R"))
```



```{r, results="hide"}
# Data
load("data/dfm.Rda")

# Dictionary LWIC Complete
LWIC_ITA <- dictionary(file = "data/large_files/Italian_LIWC2007_Dictionary.dic", 
                       format = "LIWC")
emotions <- c("Emo_Pos", "Emo_Neg", "Ansia", "Rabbia", "Tristezza", "Ottimismo" )

# Count the number of words
n.words <- c(
length(LWIC_ITA[["Emo_Pos"]]),
length(LWIC_ITA[["Emo_Neg"]]),
length(LWIC_ITA[["Ansia"]]),
length(LWIC_ITA[["Rabbia"]]),
length(LWIC_ITA[["Tristez"]]),
length(LWIC_ITA[["Ottimis"]])
)

num_words <-  data.frame(emotions,n.words)

# Extracting only the keys we need
myLWIC_ITA <- dictionary(list(positive = LWIC_ITA[["Emo_Pos"]],
                              negative = LWIC_ITA[["Emo_Neg"]],
                              anxiety = LWIC_ITA[["Ansia"]],
                              anger = LWIC_ITA[["Rabbia"]],
                              sadness = LWIC_ITA[["Tristez"]],
                              optimism = LWIC_ITA[["Ottimis"]]))

myLWIC_ITA_sent <- dictionary(list(positive = LWIC_ITA[["Emo_Pos"]],
                              negative = LWIC_ITA[["Emo_Neg"]]))
```

```{r}
kable(num_words)
```

### Group and weight the dfm

```{r}
# By party & quarter
dfm_weigh_p_quart <- dfm_group(DFM, groups = interaction(party_id, quarter))%>%
  dfm_weight(scheme = "prop")
```

## Apply the dictionary

```{r}
# Apply Dictionary to DFM
DFM_emotions <- dfm_lookup(dfm_weigh_p_quart,
                           dictionary = myLWIC_ITA)
DFM_emotions

```

### Transform the DFM into an ordinary dataframe

```{r}
data_dict_emo <- DFM_emotions %>% 
  quanteda::convert(to = "data.frame") %>% 
  cbind(docvars(DFM_emotions))

# Create a new variable with the difference of negative - positive emotions
data_dict_emo$negative_prevalence <- (data_dict_emo$negative - data_dict_emo$positive)

# Transform the proportion into percentage
data_dict_emo <- data_dict_emo %>% mutate(positive =  positive * 100,
                                          negative = negative * 100,
                                          anxiety = anxiety * 100,
                                          anger = anger *100,
                                          sadness = sadness * 100,
                                          optimism = optimism *100,
                                          negative_prevalence = negative_prevalence *100)
```

## Percentage of the emotions in time
The code is only shown for 'positive' but is identical for all emotions

```{r}
#Over time POSITIVE (quarters)
data_quarter_positive <- aggregate(x = data_dict_emo$positive,  # Specify data column
          by = list(data_dict_emo$quarter),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_quarter_positive$perc <- data_quarter_positive$x

mean_positive <- mean(data_quarter_positive$perc)

# plot 
plot_positive <- ggplot(data = data_quarter_positive, aes(x = Group.1, y = perc))+
  geom_line(color = "#00AFBB", size = 2)+
  scale_x_continuous("Quarters", labels = as.character(data_quarter_positive$Group.1), breaks = data_quarter_positive$Group.1)+
  geom_line(aes(x = Group.1, y = mean(perc)),linetype = "dashed")+
  ylab("Percentage of positive words")+
  labs(title = "Positive Emotion")
plot_positive

```
```{r, echo=FALSE, warning=FALSE}
# NEGATIVE
data_quarter_negative <- aggregate(x = data_dict_emo$negative,  # Specify data column
          by = list(data_dict_emo$quarter),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_quarter_negative$perc <- data_quarter_negative$x

# plot 
plot_negative <- ggplot(data = data_quarter_negative, aes(x = Group.1, y = perc))+
  geom_line(color = "#00AFBB", size = 2)+
  scale_x_continuous("Quarters", labels = as.character(data_quarter_negative$Group.1), breaks = data_quarter_negative$Group.1)+
  geom_line(aes(x = Group.1, y = mean(perc)), linetype = "dashed")+
  ylab("Percentage of negative words")+
  labs(title = "Negative Emotion")
plot_negative

############
# ANXIETY
data_quarter_anxiety <- aggregate(x = data_dict_emo$anxiety,  # Specify data column
          by = list(data_dict_emo$quarter),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_quarter_anxiety$perc <- data_quarter_anxiety$x

# plot
plot_anxiety <- ggplot(data = data_quarter_anxiety, aes(x = Group.1, y = perc))+
  geom_line(color = "#00AFBB", size = 2)+
  scale_x_continuous("Quarters", labels = as.character(data_quarter_anxiety$Group.1), breaks = data_quarter_anxiety$Group.1)+
  geom_line(aes(x = Group.1, y = mean(perc)), linetype = "dashed")+
  ylab("Percentage of anxious words")+
  labs(title = "Anxiety emo")
plot_anxiety

############
#ANGER
data_quarter_anger <- aggregate(x = data_dict_emo$anger,  # Specify data column
          by = list(data_dict_emo$quarter),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_quarter_anger$perc <- data_quarter_anger$x

# plot
plot_anger <- ggplot(data = data_quarter_anger, aes(x = Group.1, y = perc))+
  geom_line(color = "#00AFBB", size = 2)+
  scale_x_continuous("Quarters", labels = as.character(data_quarter_anger$Group.1), breaks = data_quarter_anger$Group.1)+
  geom_line(aes(x = Group.1, y = mean(perc)), linetype = "dashed")+
  ylab("Percentage of anger words")+
  labs(title = "Anger emo")
plot_anger

############
# SADNESS
data_quarter_sadness <- aggregate(x = data_dict_emo$sadness,  # Specify data column
          by = list(data_dict_emo$quarter),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_quarter_sadness$perc <- data_quarter_sadness$x

# plot
plot_sadness <- ggplot(data = data_quarter_sadness, aes(x = Group.1, y = perc))+
  geom_line(color = "#00AFBB", size = 2)+
  scale_x_continuous("Quarters", labels = as.character(data_quarter_sadness$Group.1), breaks = data_quarter_sadness$Group.1)+
  geom_line(aes(x = Group.1, y = mean(perc)), linetype = "dashed")+
  ylab("Percentage of sad words")+
  labs(title = "Sadness Emo")
plot_sadness

############
# OPTIMISM
data_quarter_optimism <- aggregate(x = data_dict_emo$optimism,  # Specify data column
          by = list(data_dict_emo$quarter),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_quarter_optimism$perc <- data_quarter_optimism$x

 plot
plot_optimism<- ggplot(data = data_quarter_optimism, aes(x = Group.1, y = perc))+
  geom_line(color = "#00AFBB", size = 2)+
  scale_x_continuous("Quarters", labels = as.character(data_quarter_optimism$Group.1), breaks = data_quarter_optimism$Group.1)+
  geom_line(aes(x = Group.1, y = mean(perc)), linetype = "dashed")+
  ylab("Percentage of optimistic words")+
  labs(title = "Optimism Emo")
plot_optimism

#########
# compare the levels
p1 <- ggplot() +
  # plot positive
  geom_line(data = data_quarter_positive, aes(x = Group.1, y = perc, color = "positive"), size = 2) +
  # plot negative
  geom_line(data = data_quarter_negative, aes(x = Group.1, y = perc, color = "negative"), size = 2) +
  # mean positive
  geom_line(data = data_quarter_positive, aes(x = Group.1, y = mean(perc)), linetype = "dashed") +
  # mean negative
  geom_line(data = data_quarter_negative, aes(x = Group.1, y = mean(perc)), linetype = "dashed") +
  scale_color_manual(name='Legend',
                     breaks=c('positive', 'negative'),
                     values=c('positive'='red', 'negative'='blue'))+
  scale_x_continuous("Quarters",
                     labels = as.character(data_quarter_positive$Group.1),
                     breaks = data_quarter_positive$Group.1)+
  ylab("Percentage of words")+
  labs(title = "Emotion")

p2 <- ggplot() +
  # plot anxiety
  geom_line(data = data_quarter_anxiety, aes(x = Group.1, y = perc, color = "anxiety"), size = 2) +
  # mean anxiety
  geom_line(data = data_quarter_anxiety, aes(x = Group.1, y = mean(perc)), linetype = "dashed") +
  # plot anger
  geom_line(data = data_quarter_anger, aes(x = Group.1, y = perc, color = "anger"), size = 2) +
  # mean anger
  geom_line(data = data_quarter_anger, aes(x = Group.1, y = mean(perc)), linetype = "dashed") +
  # plot sadness
  geom_line(data = data_quarter_sadness, aes(x = Group.1, y = perc, color = "sadness"), size = 2) +
  # mean sadness 
  geom_line(data = data_quarter_sadness, aes(x = Group.1, y = mean(perc)), linetype = "dashed") +
  # plot optimism
  geom_line(data = data_quarter_optimism, aes(x = Group.1, y = perc, color = "optimism"), size = 2) +
  # mean optimism 
  geom_line(data = data_quarter_optimism, aes(x = Group.1, y = mean(perc)), linetype = "dashed") +
  
  scale_color_manual(name='Legend',
                     breaks=c('anxiety', 'anger', 'sadness', 'optimism'),
                     values=c('anxiety'='red', 'anger'='blue',
                              'sadness'='green', 'optimism'= 'black'))+ 
  
  scale_x_continuous("Quarters", labels = as.character(data_quarter_positive$Group.1), breaks = data_quarter_positive$Group.1)+
  ylab("Percentage of words")+
  labs(title = "Emotions")

p1
p2

```


## Main emotion for each parliamentary group

```{r, echo=FALSE}

tstat_emo <- textstat_frequency(DFM_emotions, groups = party_id)

ggplot(data = tstat_emo, aes(x = factor(nrow(tstat_emo):1), y = frequency *100)) +
    geom_point() +
    facet_wrap(~ group, scales = "free") +
    coord_flip() +
    scale_x_discrete(breaks = nrow(tstat_emo):1,
                       labels = tstat_emo$feature) +
    labs(x = NULL, y = "Relative frequency")
```

The code is only shown for 'positive' but is identical for all emotions
```{r}

# POSITIVE
data_party_positive <- aggregate(x = data_dict_emo$positive,  # Specify data column
          by = list(data_dict_emo$party_id),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_party_positive$perc <- round(data_party_positive$x,3)
kable(data_party_positive %>% select(Group.1, perc) %>%  arrange(desc(perc)), caption = "POSITIVE")

ggplot(data=data_party_positive, aes(x=Group.1, y=perc)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=perc), vjust=0, color="black", size=3.5)+
  geom_abline(slope=0, intercept= mean(data_party_positive$perc),lty=2) +
  theme_minimal()+
  xlab("Parliamentary group")+
  labs(title = "Positive Emotion")+
  coord_flip()

```
```{r, echo=FALSE}
#By party no time (quarters)
# NEGATIVE
data_party_negative <- aggregate(x = data_dict_emo$negative,  # Specify data column
          by = list(data_dict_emo$party_id),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_party_negative$perc <- round(data_party_negative$x,3)
kable(data_party_negative %>% select(Group.1, perc) %>%  arrange(desc(perc)), caption = "NEGATIVE")

ggplot(data=data_party_negative, aes(x=Group.1, y=perc)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=perc), vjust=0, color="black", size=3.5)+
  geom_abline(slope=0, intercept= mean(data_party_negative$perc),lty=2) +
  theme_minimal()+
  coord_flip()+
  xlab("Parliamentary group")+
  labs(title = "Negative Emotion")
############################

# ANXIETY
data_party_anxiety <- aggregate(x = data_dict_emo$anxiety,  # Specify data column
          by = list(data_dict_emo$party_id),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_party_anxiety$perc <- round(data_party_anxiety$x,3)
kable(data_party_anxiety %>% select(Group.1, perc) %>%  arrange(desc(perc)), caption = "ANXIETY")

ggplot(data=data_party_anxiety, aes(x=Group.1, y=perc)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=perc), vjust=0, color="black", size=3.5)+
  geom_abline(slope=0, intercept= mean(data_party_anxiety$perc),lty=2) +
  theme_minimal()+
  coord_flip()+
  xlab("Parliamentary group")+
  labs(title = "Anxiety emotion")
##################

# ANGER
data_party_anger <- aggregate(x = data_dict_emo$anger,  # Specify data column
          by = list(data_dict_emo$party_id),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_party_anger$perc <- round(data_party_anger$x,3)
kable(data_party_anger %>% select(Group.1, perc) %>%  arrange(desc(perc)), caption = "ANGER")

ggplot(data=data_party_anger, aes(x=Group.1, y=perc)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=perc), vjust=0, color="black", size=3.5)+
  geom_abline(slope=0, intercept= mean(data_party_anger$perc),lty=2) +
  theme_minimal()+
  coord_flip()+
  xlab("Parliamentary group")+
  labs(title = "Anger emotion")
##################

# SADNESS
data_party_sadness <- aggregate(x = data_dict_emo$sadness,  # Specify data column
          by = list(data_dict_emo$party_id),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_party_sadness$perc <- round(data_party_sadness$x,3)
kable(data_party_sadness %>% select(Group.1, perc) %>%  arrange(desc(perc)), caption = "SADNESS")

ggplot(data=data_party_sadness, aes(x=Group.1, y=perc)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=perc), vjust=0, color="black", size=3.5)+
  geom_abline(slope=0, intercept= mean(data_party_sadness$perc),lty=2) +
  theme_minimal()+
  coord_flip()+
  xlab("Parliamentary group")+
  labs(title = "Sadness emotion")
##################

# OPTIMISM
data_party_optimism <- aggregate(x = data_dict_emo$optimism,  # Specify data column
          by = list(data_dict_emo$party_id),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_party_optimism$perc <- round(data_party_optimism$x,3)
kable(data_party_optimism %>% select(Group.1, perc) %>%  arrange(desc(perc)), caption = "OPTIMISM")
ggplot(data=data_party_optimism, aes(x=Group.1, y=perc)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=perc), vjust=0, color="black", size=3.5)+
    geom_abline(slope=0, intercept= mean(data_party_optimism$perc),lty=2) +
  theme_minimal()+
  coord_flip()+
  xlab("Parliamentary group")+
  labs(title = "Optimism emotion")
#################
```

### Are the average values of positive/negative emotions for each party statistically different from each other?
The reference category is PD

```{r}
# bivariate regression for check t-test 

# create the factor variables for party and quarter
data_dict_emo$factor_party <- as.factor(data_dict_emo$party_id)
data_dict_emo$factor_quarter <- as.factor(data_dict_emo$quarter)

# Check the mean values
summary(data_dict_emo$positive)
summary(data_dict_emo$negative)

# Set PD as reference category for party_id
data_dict_emo$factor_party <- relevel(data_dict_emo$factor_party, ref = "PD")
# Set 5 as reference category for quarter
data_dict_emo$factor_quarter <- relevel(data_dict_emo$factor_quarter, ref = "5")

# Run the regressions

# POSITIVE
positive_model <- lm(positive ~  factor_quarter + factor_party, data_dict_emo )
summary(positive_model)

#NEGATIVE
negative_model <- lm(negative ~  factor_quarter + factor_party, data_dict_emo )
summary(negative_model)
```

## Regressions

```{r}
# import the populism dataset
load("data/data_dict1.Rda")

# add the level of populism in the dataframe with the emotions
data_dict_emo$populism <- data_dict1$populism

# Change the reference category for quarter as quarter 8
data_dict_emo$factor_quarter <- relevel(data_dict_emo$factor_quarter, ref = "8")

# Negative prevalence
negative_prevalence_model <- lm(negative_prevalence ~ factor_party + factor_quarter + populism, data_dict_emo)
summary(negative_prevalence_model)

# Negative emotion
negative_model <- lm(negative ~ factor_party + factor_quarter + populism, data_dict_emo)
summary(negative_model)

# Anxiety emotion
anxiety_model <- lm(anxiety ~ factor_party + factor_quarter + populism, data_dict_emo)
summary(anxiety_model)

# Anger emotion
anger_model <- lm(anger ~ factor_party + factor_quarter + populism, data_dict_emo)
summary(anger_model)

# sadness emotion
sadness_model <- lm(sadness ~ factor_party + factor_quarter + populism, data_dict_emo)
summary(sadness_model)
```

### Tab the results

```{r}
tab_model(negative_model,negative_prevalence_model)
```


