---
title: 'LDA Topicmodel  '
author: "Riccardo Ruta"
date: "05/2022"
output:
  pdf_document: 
    toc: yes
    latex_engine: xelatex
  html_document: default
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
here::here("")
source(here::here("src","00_setup.R"))

```

## PART I - CREATE THE DTM

```{r, include=FALSE}
load("data/dfm_trimmed.Rda")
```

### 1) Convert the Document Feature Matrix (Dfm) in a Topic Model (Dtm)

```{r 6}
dtm <- quanteda::convert(DFM_trimmed, to = "topicmodels")
```

## PART II - FIND THE BEST NUMBER OF TOPICS K

### 1) First try K = 20:80

```{r 7, include=FALSE, eval=TRUE}
load("data/results1.Rda")
```

```{r 7.1, eval=FALSE}
## Finding the best K
top1 <- c(20:80)

## let's create an empty data frame
results1 <- data.frame(first=vector(), second=vector(), third=vector()) 
 

system.time(
  for (i  in top1) 
  { 
    set.seed(123)
    lda1 <- LDA(dtm, method= "Gibbs", k = (i),  control=list(verbose=50L, iter=100))
    topic <- (i)
    coherence <- mean(topic_coherence(lda1, dtm))
    exclusivity <- mean(topic_exclusivity(lda1))
    results1 <- rbind(results1 , cbind(topic, coherence, exclusivity ))
  }
)
# save(results1,file="data/results1.Rda")
```

```{r 7.2, echo=FALSE}
kable(head(results1))
kable(tail(results1))


plot1 <- as.ggplot(~plot(results1$coherence, results1$exclusivity,
                         main="Scatterplot K=20:80",xlab="Semantic Coherence",
                         ylab="Exclusivity ", pch=19,
                         col=ifelse(results1$coherence<=-155.8,"black","red")) +
       text(results1$coherence, results1$exclusivity,
            labels=results1$topic, cex= 1,  pos=4))

# ggsave("figs/plot_k_20-80.png", plot = plot1)
plot1
```

From this first try the best k seems to be 34

### 2) Second try K = 70:90

```{r 8, include=FALSE, eval=TRUE}
load("data/results2.Rda")
```

```{r 8.1, eval=FALSE}
top2 <- c(70:90)
top2

results2 <- data.frame(first=vector(), second=vector(), third=vector()) 
results2 

system.time(
  for (i  in top2) 
  { 
    set.seed(123)
    lda2 <- LDA(dtm, method= "Gibbs", k = (i),  control=list(verbose=50L, iter=100))
    topic <- (i)
    coherence <- mean(topic_coherence(lda2, dtm))
    exclusivity <- mean(topic_exclusivity(lda2))
    results2 <- rbind(results2 , cbind(topic, coherence, exclusivity ))
  }
)

# save(results2,file="data/results2.Rda")
```

```{r 8.2, echo=FALSE}

plot2 <- as.ggplot(~plot(results2$coherence, results2$exclusivity, main="Scatterplot K=70:90",
                         xlab="Semantic Coherence", ylab="Exclusivity ", pch=19,
                         col=ifelse(results2$coherence > -155.3,"red","black")) +
                     text(results2$coherence, results2$exclusivity,
                          labels=results2$topic, cex= 1,  pos=4))

# ggsave("figs/plot_k_70-90.png", plot = plot2)
plot2
```

In this case 84 seems better, but the plot is very dispersive

### 3) Third try K = 10:40 with iteration = 1000

```{r 9, include=FALSE}
load("data/results_k_10-40.Rda")
```

```{r 9.1, eval=FALSE}
## Finding the best K
top_k <- c(10:40)
## let's create an empty data frame
results1 <- data.frame(first=vector(), second=vector(), third=vector()) 
system.time(
  for (i  in top_k) 
  { 
    set.seed(123)
    lda1 <- LDA(dtm, method= "Gibbs", k = (i),  control=list(verbose=50L, iter=1000))
    topic <- (i)
    coherence <- mean(topic_coherence(lda1, dtm))
    exclusivity <- mean(topic_exclusivity(lda1))
    results1 <- rbind(results1 , cbind(topic, coherence, exclusivity ))
  }
)
 #save(results1,file="data/results_k_10-40.Rda")
```

```{r 9.2, echo=FALSE}
## k= 10-40
plot3 <- as.ggplot(~plot(results1$coherence, results1$exclusivity, main="Scatterplot k=10:40",
     xlab="Semantic Coherence", ylab="Exclusivity ", pch=19,
     col=ifelse(results1$coherence<=-153.9 | results1$exclusivity<9.9610 ,"black","red")) + 
       text(results1$coherence,
            results1$exclusivity, labels=results1$topic, cex= 1,  pos=4))
plot3
#ggsave("figs/plot_k_10-40.png", plot = plot3)
```

In this iteration the best choice can be 28 but the general level of coherence has fallen very low

```{r, echo =FALSE, eval = FALSE}
grid <- plot_grid(plot1, plot2, plot3,
                  labels = list("k=20:80", "k=70:90", "k=10:40"), label_x = .15, nrow = 3)

# ggsave("figs/plot_grid.png", plot = grid)
grid
```

### 4) Fourth try k = 5:20 iteration n = 2000

```{r 9.3, include=FALSE, eval=TRUE}
load("data/k_5-20.Rda")
```

```{r 9.4, eval=FALSE}
## Finding the best K
top1234 <- c(5:20)
top1234

## let's create an empty data frame
results1 <- data.frame(first=vector(), second=vector(), third=vector()) 
results1 

system.time(
  for (i  in top1234) 
  { 
    set.seed(123)
    lda1 <- LDA(dtm, method= "Gibbs", k = (i),  control=list(verbose=50L, iter=2000))
    topic <- (i)
    coherence <- mean(topic_coherence(lda1, dtm))
    exclusivity <- mean(topic_exclusivity(lda1))
    results1 <- rbind(results1 , cbind(topic, coherence, exclusivity ))
  }
)
# save(results1,file="data/k_5-20.Rda")
```

```{r 9.5, echo=FALSE}
## k= 5-20
plot4 <- as.ggplot(~plot(results1$coherence, results1$exclusivity, main="Scatterplot k=5:20",
     xlab="Semantic Coherence", ylab="Exclusivity ", pch=19,
     col=ifelse(results1$coherence<=-153.9 | results1$exclusivity<9.9610 ,"black","red")) + 
       text(results1$coherence,
            results1$exclusivity, labels=results1$topic, cex= 1,  pos=4))
plot4
#ggsave("figs/plot_k_5-20.png", plot = plot4)
```

```{r 9.6}
grid2 <- plot_grid(plot1, plot2, plot3, plot4,
                  labels = list("k=20:80", "k=70:90", "k=10:40", "k=5:20"), label_x = .15, nrow = 3)

# ggsave("figs/plot_grid2.png", plot = grid2)
grid2
```

```{r 9.7, echo=FALSE}
plot1
plot2
plot3
plot4
```

After all these tests, I believe that 10 is the best choice because it achieves good levels of coherence and exclusivity and is consistent with the choice of looking for substantive policy themes

### 5) Fifth try k = 10:50 iteration n = 1000

```{r 9.8.1, include=FALSE, eval=TRUE}
load("data/results_k_10-50.Rda")
```

```{r 9.8.2, eval = FALSE}
# 10 : 50 iter 10
top1 <- c(10:50)

## let's create an empty data frame
risultati <- data.frame(first=vector(), second=vector(), third=vector()) 

system.time(
  for (i  in top1) 
  { 
    set.seed(123)
    lda_test <- LDA(dtm, method= "Gibbs", k = (i),
                    control=list(verbose=50L, iter=1000))
    topic <- (i)
    coherence_test <- mean(topic_coherence(lda_test, dtm))
    exclusivity_test <- mean(topic_exclusivity(lda_test))
    risultati <- rbind(risultati,
                       cbind(topic, coherence_test, exclusivity_test ))
  }
)
# save(risultati,file="data/results_K_10-50.Rda")
```

```{r 9.9, echo=FALSE}
## k= 5-20
plot5 <- as.ggplot(~plot(risultati$coherence_test, risultati$exclusivity_test, main="Scatterplot k=10:50",
     xlab="Semantic Coherence", ylab="Exclusivity ", pch=19,
     col=ifelse(risultati$coherence_test<=-7 | risultati$exclusivity_test<9.7 ,"black","red")) + 
       text(risultati$coherence_test,
            risultati$exclusivity_test, labels=risultati$topic, cex= 1,  pos=4))
plot5
# ggsave("figs/plot_k_10-50.png", plot = plot5)
```

## PART III - ANALISYS OF THE TOPICS

### First try with k = 30

```{r 10, include=FALSE, eval=TRUE}
load("data/lda_k_30.Rda")
```

```{r 10.1, eval=FALSE}
system.time(lda <- LDA(dtm, method= "Gibbs", k = 30, control = list(seed = 123)))
# save(lda, file = "data/lda_k_30.Rda")
```

### Here i extract the most important terms from the model

```{r 11, echo=FALSE}
terms <- get_terms(lda, 10)
dt1 <- terms[,1:10]
dt2 <- terms[,11:20]
dt3 <- terms[,21:30]


knitr::kable(dt1, col.names = c("Top terms 01","Top terms 02","Top terms 03",
                         "Top terms 04","Top terms 05","Top terms 06","Top terms 07","Top terms 08","Top terms 09","Top terms 10"))%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))

knitr::kable(dt2, col.names = c("Top terms 11","Top terms 12","Top terms 13",
                         "Top terms 14","Top terms 15","Top terms 16","Top terms 17","Top terms 18","Top terms 19","Top terms 20"))%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))

knitr::kable(dt3, col.names = c("Top terms 21","Top terms 22","Top terms 23",
                         "Top terms 24","Top terms 25","Top terms 26","Top terms 27","Top terms 28","Top terms 29","Top terms 30"))%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))
```

### $$COMMENT HERE$$

```{r 12, echo=FALSE}
titles <- c("1", "2", "3", "4", "5", "6", "7", "8",
            "9", "10","11", "12","13", "14", "15", "16",
            "17", "18", "19", "20",
            "21", "22","23",
            "24", "25", "26", "27", "28", "29", "30")

table_titles <- rbind (titles, terms)

t1 <- table_titles[,1:10]
t2 <- table_titles[,11:20]
t3 <- table_titles[,21:30]

kable(t1)%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))

kable(t2)%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))

kable(t3)%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))
```

### $$COMMENT HERE$$

### Repeat the search using a much lower K.

### K = 10

```{r 13, include=FALSE}
load("data/lda_k_10.Rda")
```

```{r 14, eval=FALSE}
system.time(lda_k_10 <- LDA(dtm, method= "Gibbs", k = 10, control = list(seed = 123)))
# save(lda_k_10, file = "data/lda_k_30.Rda")
```

```{r 15, echo=FALSE}
terms <- get_terms(lda_k_10, 10)
dt1 <- terms[,1:10]


knitr::kable(dt1, col.names = c("Top terms 01","Top terms 02","Top terms 03",
                         "Top terms 04","Top terms 05","Top terms 06","Top terms 07","Top terms 08","Top terms 09","Top terms 10"))%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))
```

### $$COMMENT HERE$$

### Titles:

```{r 16, echo=FALSE}
titles <- c("1", "2", "CORONAVIRUS", "SOSTEGNI ECONOMICI", "LEGA", "DIRITTI", "GOVERNO", "INFORMAZIONE GIORNALISTICA",
            "9", "10")

table_titles <- rbind (titles, terms)

t1 <- table_titles[,1:10]

kable(t1)%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))

```

### $$COMMENT HERE$$

### Repeat the search using a much lower K.

### K = 5

```{r 17, include=FALSE}
load("data/lda_k_5.Rda")
```

```{r 18, eval=FALSE}
system.time(lda_k_5 <- LDA(dtm, method= "Gibbs", k = 5, control = list(seed = 123)))
# save(lda_k_5, file = "data/lda_k_5.Rda")
```

```{r 19, echo=FALSE}
terms <- get_terms(lda_k_5, 10)
dt1 <- terms[,1:5]


knitr::kable(dt1, col.names = c("Top terms 01","Top terms 02","Top terms 03",
                         "Top terms 04","Top terms 05"))%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))
```

### $$COMMENT HERE$$

### Titles:

```{r 20, echo=FALSE}
titles <- c("1", "2", "3", "4", "5")

table_titles <- rbind (titles, terms)

t1 <- table_titles[,1:5]

kable(t1)%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))

```

### $$COMMENT HERE$$

## Final try k = 22

### Try with k = 22

```{r 30, include=FALSE, eval=TRUE}
load("data/lda_k_22.Rda")
```

```{r 30.1, eval=FALSE}
system.time(lda_22 <- LDA(dtm, method= "Gibbs", k = 22, control = list(seed = 123)))
# save(lda, file = "data/lda_k_22.Rda")
```

### Here i extract the most important terms from the model

```{r 30.2, echo=FALSE}
terms <- get_terms(lda_22, 10)
dt1 <- terms[,1:6]
dt2 <- terms[,7:12]
dt3 <- terms[,13:18]
dt4 <- terms[,19:22]


knitr::kable(dt1, col.names = c("Top terms 01","Top terms 02","Top terms 03",
                         "Top terms 04","Top terms 05","Top terms 06"))%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))

knitr::kable(dt2, col.names = c("Top terms 7","Top terms 8","Top terms 9",
                                "Top terms 10","Top terms 11","Top terms 12"))%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))

knitr::kable(dt3, col.names = c("Top terms 13","Top terms 14","Top terms 15",
                         "Top terms 16","Top terms 17","Top terms 18"))%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))

knitr::kable(dt4, col.names = c("Top terms 19","Top terms 20","Top terms 21",
                         "Top terms 22"))%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))

```
