---
title: 'LDA Topicmodel  '
author: "Riccardo Ruta"
date: "05/2022"
output:
  pdf_document: 
    toc: yes
    latex_engine: xelatex
  html_document: default
  word_document:
    toc: yes
---

```{r setup4, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
here::here("")
source(here::here("src","00_setup.R"))

```

# LDA Topic model analysis

## CREATE THE DTM

```{r, include=FALSE}
load("data/dfm_trimmed.Rda")
```

### Remove all the account's mentions

```{r}
DFM_trimmed@Dimnames$features <- gsub("^@", "", DFM_trimmed@Dimnames$features)
```

###Convert the Document Feature Matrix (Dfm) in a Topic Model (Dtm)

```{r 6, eval=FALSE}
dtm <- quanteda::convert(DFM_trimmed, to = "topicmodels")
```



## FIND THE BEST NUMBER OF TOPICS K

### Search the best number of Topics comparing coherence and exclusivity values
 K = 10:50

```{r 7, include=FALSE, eval=TRUE}
load("data/results_k_10-50.Rda")
```

```{r 7.1, eval=FALSE}
# 10 : 50 iter 1000
top1 <- c(10:50)

## let's create an empty data frame
risultati <- data.frame(first=vector(), second=vector(), third=vector()) 

system.time(
  for (i  in top1) 
  { 
    set.seed(123)
    lda_test <- LDA(dtm, method= "Gibbs", k = (i),  control=list(verbose=50L, iter=1000))
    topic <- (i)
    coherence_test <- mean(topic_coherence(lda_test, dtm))
    exclusivity_test <- mean(topic_exclusivity(lda_test))
    risultati <- rbind(risultati , cbind(topic, coherence_test, exclusivity_test ))
  }
)
# save(risultati,file="data/results_K_10-50.Rda")

```

### Plot the values of coherence and exclusivity in order to find the best K
```{r 7.2, echo=FALSE}
# VISUALIZE RESULTS
plot5 <- as.ggplot(~plot(risultati$coherence_test, risultati$exclusivity_test, main="Scatterplot k=10:50",
                         xlab="Semantic Coherence", ylab="Exclusivity ", pch=19,
                         col=ifelse(risultati$coherence_test > -265 & risultati$exclusivity_test>10.40 ,"red","black")) + 
                     text(risultati$coherence_test,
                          risultati$exclusivity_test, labels=risultati$topic, cex= 1,  pos=4))
plot5
```

Interpreting those data i can state that K= 11 has the best values of coherence and exclusivity.

\newpage

## ANALISYS OF THE TOPICS

### Repeat the analysis selecting k = 11

```{r 30, include=FALSE, eval=TRUE}
load("data/lda_k_11.Rda")
```

```{r 30.1, eval=FALSE}
system.time(lda_11 <- LDA(dtm, method= "Gibbs", k = 11, control = list(seed = 123)))
# save(lda_11, file = "data/lda_k_11.Rda")
```

### The most important terms from the model, for each topic

```{r 30.2, echo=FALSE}
terms <- get_terms(lda_11, 10)
dt1 <- terms[,1:6]
dt2 <- terms[,7:11]


knitr::kable(dt1, col.names = c("Top terms 01","Top terms 02","Top terms 03",
                         "Top terms 04","Top terms 05","Top terms 06"))%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))

knitr::kable(dt2, col.names = c("Top terms 7","Top terms 8","Top terms 9",
                                "Top terms 10","Top terms 11"))%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))

```

```{r}
titles_11 <- c("1", "2", "3", "4", "5","6",
                 "7", "8", "9", "10", "11")

table_titles_11 <- rbind (titles_11, terms)


t11.1 <- table_titles_11[,1:6]
t11.2 <- table_titles_11[,7:11]

kable(t11.1)%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))
kable(t11.2)%>%
  kable_styling(latex_options = c("HOLD_position","scale_down"))

```

