---
title: "LDA Topicmodel  "
author: "Riccardo Ruta riccardo.ruta@studenti.unimi.it"
date: "06/05/2022"
output:
  pdf_document: 
    toc: yes
    latex_engine: xelatex
  html_document: default
---

```{r setup, include=FALSE}
here::here("")
source(here::here("src","00_setup.R"))

```

## PART I - CREATE THE DTM

### 1) Import and clean dataset

```{r summary, results="hide"}
# import the data
tw <-  read_csv("data/large_files/politicians_all_final_tweets.csv",show_col_types = FALSE)

# Adjust datetime (Run code in this order!)
Sys.setlocale("LC_TIME", "C")
tw$date <- as.Date(strptime(tw$creato_il,"%a %b %d %H:%M:%S %z %Y", tz = "CET"))
tw$date <- na.replace(tw$date, as.Date(tw$creato_il))

# Create week variable
tw <- tw %>% mutate(week = cut.Date(date, breaks = "1 week", labels = FALSE))

# Create month variable
tw <- tw %>% mutate(month = cut.Date(date, breaks = "1 month", labels = FALSE))

# Remove missing from tweets column (using remove_na tidyverse)
tw <- tw %>% drop_na(tweet_testo)

# Remove space from genere variable
a <- unique(tw$genere)
tw$genere <- gsub(a[3],"male",tw$genere)

# Select variables for the analysis
dataset <- tw %>% select(nome, tweet_testo, genere, party_id,chamber,status, date, week, month )

```

### 2) Create the corpus

```{r 1}
corp <- corpus(dataset, text = "tweet_testo")
```

### 3) Create the Dfm removing stopwords and trimming

```{r 3, message=FALSE, warning=FALSE}
my_word <- as.list(read_csv("data/it_stopwords_new_list.csv", show_col_types = FALSE))

my_list <- c("🇮🇹","c'è","+","🔴",my_word$stopwords, stopwords('italian'))

rev_dfm <- dfm(tokens(corp, remove_symbols = TRUE, remove_url = TRUE),
               remove = my_list, tolower = TRUE,
               remove_punct = TRUE, remove_numbers=TRUE)

rev_dfm <-   dfm_trim(rev_dfm, min_termfreq = 0.95, termfreq_type = "quantile",
                      max_docfreq = 0.1, docfreq_type = "prop")

rev_dfm <- dfm_group(rev_dfm, groups= month)
```

```{r 4}
topfeatures(rev_dfm, 20)
kable(topfeatures(rev_dfm, 20),col.names = "topfeature")
```

### 4) Convert the Document Feature Matrix (Dfm) in a Topic Model (Dtm)

```{r 6}
dtm <- quanteda::convert(rev_dfm, to = "topicmodels")
```

## PART II - FIND THE BEST NUMBER OF TOPICS K

### 1) First try K = 20:80

```{r 7, include=FALSE, eval=TRUE}
load("data/results1.Rda")
```

```{r 7.1, eval=FALSE}
## Finding the best K
top1 <- c(20:80)

## let's create an empty data frame
results1 <- data.frame(first=vector(), second=vector(), third=vector()) 
 

system.time(
  for (i  in top1) 
  { 
    set.seed(123)
    lda1 <- LDA(dtm, method= "Gibbs", k = (i),  control=list(verbose=50L, iter=100))
    topic <- (i)
    coherence <- mean(topic_coherence(lda1, dtm))
    exclusivity <- mean(topic_exclusivity(lda1))
    results1 <- rbind(results1 , cbind(topic, coherence, exclusivity ))
  }
)
# save(results1,file="data/results1.Rda")
```

```{r 7.2, echo=FALSE}
kable(head(results1))
kable(tail(results1))


plot1 <- as.ggplot(~plot(results1$coherence, results1$exclusivity,
                         main="Scatterplot K=20:80",xlab="Semantic Coherence",
                         ylab="Exclusivity ", pch=19,
                         col=ifelse(results1$coherence<=-155.8,"black","red")) +
       text(results1$coherence, results1$exclusivity,
            labels=results1$topic, cex= 1,  pos=4))

# ggsave("figs/plot_k_20-80.png", plot = plot1)
plot1
```

From this first try it's seems that the correct number of K is ......

### 2) Second try K = 70:90

```{r 8, include=FALSE, eval=TRUE}
load("data/results2.Rda")
```

```{r 8.1, eval=FALSE}
top2 <- c(70:90)
top2

results2 <- data.frame(first=vector(), second=vector(), third=vector()) 
results2 

system.time(
  for (i  in top2) 
  { 
    set.seed(123)
    lda2 <- LDA(dtm, method= "Gibbs", k = (i),  control=list(verbose=50L, iter=100))
    topic <- (i)
    coherence <- mean(topic_coherence(lda2, dtm))
    exclusivity <- mean(topic_exclusivity(lda2))
    results2 <- rbind(results2 , cbind(topic, coherence, exclusivity ))
  }
)

# save(results2,file="data/results2.Rda")
```

```{r 8.2, echo=FALSE}
kable(results2)

plot2 <- as.ggplot(~plot(results2$coherence, results2$exclusivity, main="Scatterplot K=70:90",
                         xlab="Semantic Coherence", ylab="Exclusivity ", pch=19,
                         col=ifelse(results2$coherence > -155.3,"red","black")) +
                     text(results2$coherence, results2$exclusivity,
                          labels=results2$topic, cex= 1,  pos=4))

# ggsave("figs/plot_k_70-90.png", plot = plot2)
plot2
```

In this case ... seems better than ...

### 3) Third try K = 10:40 with iteration = 1000

```{r 9, include=FALSE}
load("data/results_k_10-40.Rda")
```

```{r 9.1, eval=FALSE}
## Finding the best K
top_k <- c(10:40)
## let's create an empty data frame
results1 <- data.frame(first=vector(), second=vector(), third=vector()) 
system.time(
  for (i  in top_k) 
  { 
    set.seed(123)
    lda1 <- LDA(dtm, method= "Gibbs", k = (i),  control=list(verbose=50L, iter=1000))
    topic <- (i)
    coherence <- mean(topic_coherence(lda1, dtm))
    exclusivity <- mean(topic_exclusivity(lda1))
    results1 <- rbind(results1 , cbind(topic, coherence, exclusivity ))
  }
)
 #save(results1,file="data/results_k_10-40.Rda")
```

```{r 9.2, echo=FALSE}
kable(results1)

## k= 10-40
plot3 <- as.ggplot(~plot(results1$coherence, results1$exclusivity, main="Scatterplot k=10:40",
     xlab="Semantic Coherence", ylab="Exclusivity ", pch=19,
     col=ifelse(results1$coherence<=-153.9 | results1$exclusivity<9.9610 ,"black","red")) + 
       text(results1$coherence,
            results1$exclusivity, labels=results1$topic, cex= 1,  pos=4))
plot3
#ggsave("figs/plot_k_10-40.png", plot = plot3)

grid <- plot_grid(plot1, plot2, plot3,
                  labels = list("k=20:80", "k=70:90", "k=10:40"), label_x = .15, nrow = 3)

# ggsave("figs/plot_grid.png", plot = grid)
grid
```

### 4) Fourth try k = 5:20 iteration n = 2000

```{r 9.3, include=FALSE, eval=TRUE}
load("data/k_5-20.Rda")
```

```{r 9.4, eval=FALSE}
## Finding the best K
top1234 <- c(5:20)
top1234

## let's create an empty data frame
results1 <- data.frame(first=vector(), second=vector(), third=vector()) 
results1 

system.time(
  for (i  in top1234) 
  { 
    set.seed(123)
    lda1 <- LDA(dtm, method= "Gibbs", k = (i),  control=list(verbose=50L, iter=2000))
    topic <- (i)
    coherence <- mean(topic_coherence(lda1, dtm))
    exclusivity <- mean(topic_exclusivity(lda1))
    results1 <- rbind(results1 , cbind(topic, coherence, exclusivity ))
  }
)
# save(results1,file="data/k_5-20.Rda")
```

```{r 9.5, echo=FALSE}
kable(results1)

## k= 5-20
plot4 <- as.ggplot(~plot(results1$coherence, results1$exclusivity, main="Scatterplot k=5:20",
     xlab="Semantic Coherence", ylab="Exclusivity ", pch=19,
     col=ifelse(results1$coherence<=-153.9 | results1$exclusivity<9.9610 ,"black","red")) + 
       text(results1$coherence,
            results1$exclusivity, labels=results1$topic, cex= 1,  pos=4))
plot4
#ggsave("figs/plot_k_5-20.png", plot = plot4)

grid2 <- plot_grid(plot1, plot2, plot3, plot4,
                  labels = list("k=20:80", "k=70:90", "k=10:40", "k=5:20"), label_x = .15, nrow = 3)

# ggsave("figs/plot_grid2.png", plot = grid2)
grid2
```

```{r 9.6, echo=FALSE}
plot1
plot2
plot3
plot4
```

### After this try i can state that 30(81) is the best choice

## PART III - ANALISYS OF THE TOPICS

```{r 10, include=FALSE, eval=TRUE}
load("data/lda_k_30.Rda")
```

```{r 10.1, eval=FALSE}
system.time(lda <- LDA(dtm, method= "Gibbs", k = 30, control = list(seed = 123)))
# save(lda, file = "data/lda_k_30.Rda")
```

### Here i extract the most important terms from the model

```{r 11, echo=FALSE}
terms <- get_terms(lda, 10)
dt1 <- terms[,1:10]
dt2 <- terms[,11:20]
dt3 <- terms[,21:30]


knitr::kable(dt1, col.names = c("Top terms 01","Top terms 02","Top terms 03",
                         "Top terms 04","Top terms 05","Top terms 06","Top terms 07","Top terms 08","Top terms 09","Top terms 10"))%>%
  kable_styling(latex_options = "scale_down")

knitr::kable(dt2, col.names = c("Top terms 11","Top terms 12","Top terms 13",
                         "Top terms 14","Top terms 15","Top terms 16","Top terms 17","Top terms 18","Top terms 19","Top terms 20"))%>%
  kable_styling(latex_options = "scale_down")

knitr::kable(dt3, col.names = c("Top terms 21","Top terms 22","Top terms 23",
                         "Top terms 24","Top terms 25","Top terms 26","Top terms 27","Top terms 28","Top terms 29","Top terms 30"))%>%
  kable_styling(latex_options = "scale_down")
```

### Using 30 topics I imagined that..... COMMENT HERE

```{r 12, echo=FALSE}
titles <- c("1", "2", "3", "4", "5", "6", "7", "8",
            "9", "10","11", "12","13", "14", "15", "16",
            "17", "18", "19", "20",
            "21", "22","23",
            "24", "25", "26", "27", "28", "29", "30")

table_titles <- rbind (titles, terms)

t1 <- table_titles[,1:10]
t2 <- table_titles[,11:20]
t3 <- table_titles[,21:30]

kable(t1)%>%
  kable_styling(latex_options = "scale_down")

kable(t2)%>%
  kable_styling(latex_options = "scale_down")

kable(t3)%>%
  kable_styling(latex_options = "scale_down")
```

### This method turns out to be cumbersome and not very informative because for many "topics" it is difficult for me to find a label.

### So, I also decided to repeat the search using a much lower K.

```{r 13, include=FALSE}
load("data/lda_k_10.Rda")
```

```{r 14, eval=FALSE}
system.time(lda_k_10 <- LDA(dtm, method= "Gibbs", k = 10, control = list(seed = 123)))
# save(lda, file = "data/lda_k_30.Rda")
```

```{r 15, echo=FALSE}
terms <- get_terms(lda_k_10, 10)
dt1 <- terms[,1:10]


knitr::kable(dt1, col.names = c("Top terms 01","Top terms 02","Top terms 03",
                         "Top terms 04","Top terms 05","Top terms 06","Top terms 07","Top terms 08","Top terms 09","Top terms 10"))%>%
  kable_styling(latex_options = "scale_down")
```

### Titles:

```{r 16, echo=FALSE}
titles <- c("1", "2", "3", "4", "5", "6", "7", "8",
            "9", "10")

table_titles <- rbind (titles, terms)

t1 <- table_titles[,1:10]

kable(t1)%>%
  kable_styling(latex_options = "scale_down")

```

## PART IV - RE-ANALISYS OF THE TOPICS as GENRE

```{=tex}
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
```
I produced this pdf by filling out an R-Markdown, here i paste my complete script:

```{r script, eval=FALSE}
################################
## EXERCISE 4 --> TOPIC MODEL ##
################################

library(quanteda.textmodels)
library(quanteda)
library(topicmodels)
library(topicdoc)
library(cowplot)
library(ggplot2)
library(ggplotify)
library(knitr)
library(tibble)
library(kableExtra)

getwd()
setwd("C:/Users/Riccardo/Documents/UNIVERSITA'/MAGISTRALE/Big Data Analysis/LAB4/assignment_4")
getwd()

## Open the file with movie reviews inside the quanteda.textmodels package
data("data_corpus_moviereviews",
     package ="quanteda.textmodels")

## Create the corpus
corp <- tail(data_corpus_moviereviews,500) + 
  head(data_corpus_moviereviews, 500)

## Extract the actual texts of the movie reviews and adding them as docvars in the corpus
docvars(corp, "texts") <- texts(corp)

## Create the Dfm removing stopwords
rev_dfm <- dfm(corp, remove =c(stopwords("english"), ("+"), ("<"), (">"),
                               ("rt"), ("00*"),("="),
                               ("`"), ("d"), ("r"), ("t"), ("m"), ("l"),
                               ("b"), ("g"), ("$"), ("j"), ("o"), ("u"),
                               ("e")), tolower = TRUE, stem = FALSE,
                remove_punct = TRUE, remove_numbers=TRUE)

## Timming the Dfm
rev_dfm <-   dfm_trim(rev_dfm, min_termfreq = 0.95, termfreq_type = "quantile", 
                       max_docfreq = 0.1, docfreq_type = "prop")

kable(topfeatures(rev_dfm, 20))

## Keeping only documents with number of tokens >0
rev_dfm[ntoken(rev_dfm) == 0,]
rev_dfm <- rev_dfm[ntoken(rev_dfm) > 0,]

str(rev_dfm@docvars)

## Convert the Document Feature Matrix (Dfm) in a Topic Model (Dtm)
dtm <- convert(rev_dfm, to = "topicmodels")

###################################################################################
## Finding the best K
top1 <- c(20:80)
top1

## let's create an empty data frame
results1 <- data.frame(first=vector(), second=vector(), third=vector()) 
results1 

system.time(
  for (i  in top1) 
  { 
    set.seed(123)
    lda1 <- LDA(dtm, method= "Gibbs", k = (i),  control=list(verbose=50L,
                                                             iter=100))
    topic <- (i)
    coherence <- mean(topic_coherence(lda1, dtm))
    exclusivity <- mean(topic_exclusivity(lda1))
    results1 <- rbind(results1 , cbind(topic, coherence, exclusivity ))
  }
)
# save(results1,file="data/results1.Rda")
# load("data/results1.Rda")

kable(head(results1))
kable(tail(results1))
str(results1)


plot1 <- as.ggplot(~plot(results1$coherence, results1$exclusivity, main="Scatterplot K=20:80",
     xlab="Semantic Coherence", ylab="Exclusivity ", pch=19, col=ifelse(results1$coherence<=-155.8,"black","red")) +
       text(results1$coherence, results1$exclusivity,
            labels=results1$topic, cex= 1,  pos=4))

# ggsave("figs/plot1.png", plot = plot1)
plot1

## From this first try it's seems that the correct number of K is close to 71

###################################################################################
## Now i repeat the procedure with 70:90 

top2 <- c(70:90)
top2

results2 <- data.frame(first=vector(), second=vector(), third=vector()) 
results2 

system.time(
  for (i  in top2) 
  { 
    set.seed(123)
    lda2 <- LDA(dtm, method= "Gibbs", k = (i),  control=list(verbose=50L,
                                                             iter=100))
    topic <- (i)
    coherence <- mean(topic_coherence(lda2, dtm))
    exclusivity <- mean(topic_exclusivity(lda2))
    results2 <- rbind(results2 , cbind(topic, coherence, exclusivity ))
  }
)

# save(results2,file="data/results2.Rda")
# load("data/results2.Rda")

kable(results2)
str(results2)


plot2 <- as.ggplot(~plot(results2$coherence, results2$exclusivity, main="Scatterplot K=70:90",
                         xlab="Semantic Coherence", ylab="Exclusivity ", pch=19,
                         col=ifelse(results2$coherence > -155.3,"red","black")) +
                     text(results2$coherence, results2$exclusivity, labels=results2$topic, cex= 1,  pos=4))

# ggsave("figs/plot2.png", plot = plot2)
plot2
## 81 seems better than 71

##################################################################################
## now i repeat the cycle with the correct number of iteration (2000) for 75:85

top3 <- c(75:95)
top3

results3 <- data.frame(first=vector(), second=vector(), third=vector()) 
results3 

system.time(
  for (i  in top3) 
  { 
    set.seed(123)
    lda3 <- LDA(dtm, method= "Gibbs", k = (i), control=list(verbose=50L,
                                                            iter=2000))
    topic <- (i)
    coherence <- mean(topic_coherence(lda3, dtm))
    exclusivity <- mean(topic_exclusivity(lda3))
    results3 <- rbind(results3 , cbind(topic, coherence, exclusivity ))
  }
)

# save(results3,file="data/results3.Rda")
# load("data/results3.Rda")

kable(results3)
str(results3)

## k=81
plot3 <- as.ggplot(~plot(results3$coherence, results3$exclusivity, main="Scatterplot k=75:95",
     xlab="Semantic Coherence", ylab="Exclusivity ", pch=19, col=ifelse(results3$coherence<=-153.9 | results3$exclusivity<9.9610 ,"black","red")) +
       
       text(results3$coherence, results3$exclusivity,
            labels=results3$topic, cex= 1,  pos=4))
plot3
#ggsave("figs/plot3.png", plot = plot3)

grid <- plot_grid(plot1, plot2, plot3, labels = list("k=20:80", "k=70:90",
                                                     "k=75:95"),
                  label_x = .15, nrow = 3)

grid
# ggsave("figs/plot_grid.png", plot = grid)

## After this try i can state that 81 is the best choice

#################################################################################################
load("data/lda.Rda")
# system.time(lda <- LDA(dtm, method= "Gibbs", k = 81, control = list(seed = 123)))
# save(lda, file = "data/lda.Rda")

## Here i extract the most important terms from the model

terms <- get_terms(lda, 10)

dt1 <- terms[,1:10]
dt2 <- terms[,11:20]
dt3 <- terms[,21:30]
dt4 <- terms[,31:40]
dt5 <- terms[,41:50]
dt6 <- terms[,51:60]
dt7 <- terms[,61:70]
dt8 <- terms[,71:81]


knitr::kable(dt1, col.names = c("Top terms 01","Top terms 02","Top terms 03",
                         "Top terms 04","Top terms 05","Top terms 06","Top terms 07","Top terms 08","Top terms 09","Top terms 10"))%>%
  kable_styling(latex_options = "scale_down")

knitr::kable(dt2, col.names = c("Top terms 11","Top terms 12","Top terms 13",
                         "Top terms 14","Top terms 15","Top terms 16","Top terms 17","Top terms 18","Top terms 19","Top terms 20"))%>%
  kable_styling(latex_options = "scale_down")

knitr::kable(dt3, col.names = c("Top terms 21","Top terms 22","Top terms 23",
                         "Top terms 24","Top terms 25","Top terms 26","Top terms 27","Top terms 28","Top terms 29","Top terms 30"))%>%
  kable_styling(latex_options = "scale_down")

knitr::kable(dt4, col.names = c("Top terms 31","Top terms 32","Top terms 33",
                         "Top terms 34","Top terms 35","Top terms 36","Top terms 37","Top terms 38","Top terms 39","Top terms 40"))%>%
  kable_styling(latex_options = "scale_down")

knitr::kable(dt5, col.names = c("Top terms 41","Top terms 42","Top terms 43",
                         "Top terms 44","Top terms 45","Top terms 46","Top terms 47","Top terms 48","Top terms 49","Top terms 50"))%>%
  kable_styling(latex_options = "scale_down")

knitr::kable(dt6, col.names = c("Top terms 51","Top terms 52","Top terms 53",
                         "Top terms 54","Top terms 55","Top terms 56","Top terms 57","Top terms 58","Top terms 59","Top terms 60"))%>%
  kable_styling(latex_options = "scale_down")

knitr::kable(dt7, col.names = c("Top terms 61","Top terms 62","Top terms 63",
                         "Top terms 64","Top terms 65","Top terms 66","Top terms 67","Top terms 68","Top terms 69","Top terms 70"))%>%
  kable_styling(latex_options = "scale_down")

knitr::kable(dt8, col.names = c("Top terms 71","Top terms 72","Top terms 73",
                         "Top terms 74","Top terms 75","Top terms 76","Top terms 77","Top terms 78","Top terms 79","Top terms 80","top terms 81"))%>%
  kable_styling(latex_options = "scale_down")


titles <- c("shakespeare", "armageddon", "3", "the usual sospects", "seven", "shrek", "7", "8", "9", "10",
            "11", "austin powers","griffin", "14", "15", "16", "the batman", "18", "19", "20",
            "godzilla", "22","the grat lebowski", "24", "25", "26", "27", "28", "29", "wonderful christmas",
            "patch adams", "32","tommy lee jones", "34", "35", "36", "37", "38", "39", "40",
            "mission impossible", "42","ted", "teen", "45", "eddie murphy", "47", "48", "49", "50",
            "the truman show", "52","song", "special effect", "55", "56", "disney cartoon", "john travolta", "jackie chan", "60",
            "61", "62","bill campbell", "64", "Saving private Ryan", "pulp fiction", "67", "aliens", "69", "70",
            "rocky", "72","73", "74", "75", "76", "77", "78", "79", "80", "81"
            )

table_titles <- rbind (titles, terms)

t1 <- table_titles[,1:10]
t2 <- table_titles[,11:20]
t3 <- table_titles[,21:30]
t4 <- table_titles[,31:40]
t5 <- table_titles[,41:50]
t6 <- table_titles[,51:60]
t7 <- table_titles[,61:70]
t8 <- table_titles[,71:81]

kable(t1)%>%
  kable_styling(latex_options = "scale_down")

kable(t1)%>%
  kable_styling(latex_options = "scale_down")

kable(t1)%>%
  kable_styling(latex_options = "scale_down")

kable(t1)%>%
  kable_styling(latex_options = "scale_down")

kable(t1)%>%
  kable_styling(latex_options = "scale_down")

kable(t1)%>%
  kable_styling(latex_options = "scale_down")

kable(t1)%>%
  kable_styling(latex_options = "scale_down")

kable(t1)%>%
  kable_styling(latex_options = "scale_down")

##################################################################################
## Repeat the procedure with K = 3:15 looking for film genre

genere <- c(3:15)

results.genere <- data.frame(first=vector(), second=vector(), third=vector()) 

system.time(
  for (i  in genere) 
  { 
    set.seed(123)
    lda.genere <- LDA(dtm, method= "Gibbs", k = (i),  control=list(verbose=50L, iter=100))
    topic <- (i)
    coherence <- mean(topic_coherence(lda.genere, dtm))
    exclusivity <- mean(topic_exclusivity(lda.genere))
    results.genere <- rbind(results.genere , cbind(topic,
                                                   coherence, exclusivity ))
  }
)

# save(results.genere,file="data/results_genere.Rda")
# load("data/results_genere.Rda")

plot.genere <- as.ggplot(~plot(results.genere$coherence,
                               results.genere$exclusivity, main="Scatterplot K=3:9",xlab="Semantic Coherence", ylab="Exclusivity ", pch=19,
                         col=ifelse(results.genere$coherence > -155.3,"red","black")) + text(results.genere$coherence, results.genere$exclusivity,
                                                                                             labels=results.genere$topic, cex= 1,  pos=4))


# ggsave("figs/plot_genere.png", plot = plot.genere)

plot.genere


compar <- plot_grid(plot3, plot.genere, label_x = .15, ncol = 2 )

compar
# ggsave("figs/plot_compar.png", plot = compar)

##################################################################################
## Looking for topics = genre 6 seems to be the best choice

load("data/lda_genere.Rda")
# system.time(lda.genere <- LDA(dtm, method= "Gibbs", k = 6, control = list(seed = 123)))
# save(lda.genere, file = "data/lda_genere.Rda")

## Extract the 15 most important terms from the model

terms2 <- get_terms(lda.genere, 15)

A <- kable(terms2, col.names = c("Top terms genre1", "Top terms genre2", "Top terms genre3", "Top terms genre4", "Top terms genre5", "Top terms genre6"))
A

B <-kable(terms2, col.names = c("Action", "Thriller", "Comedy", "Fantasy", "Family", "Romance"))
B
```
