---
title: "Dictionary Analysis"
author: "Riccardo Ruta"
date: "7/5/2022"
output: 
  pdf_document:
    toc: yes
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("src","00_setup.R"))
```

### RICORSO ALLA RETORICA POPULISTA.

### A livello di partiti politici, quali fanno maggiormente ricorso alla retorica populista?

### A livello di singoli politici, quali fanno maggiormente ricorso alla retorica populista?

Per rispondere a questa domanda, ricorrere ai seguenti dizionari 3(+1) dizionari:

-   Rooduijn & Pauwels: Rooduijn, M., and T. Pauwels. 2011. "Measuring Populism: Comparing Two Methods of Content Analysis." West European Politics 34 (6): 1272--1283.

-   Decadri & Boussalis: Decadri, S., & Boussalis, C. (2020). Populism, party membership, and language complexity in the Italian chamber of deputies. Journal of Elections, Public Opinion and Parties, 30(4), 484-503.

-   Grundl: Gründl J. Populist ideas on social media: A dictionary-based measurement of populist communication. New Media & Society. December 2020.

-   Decadri & Boussalis + Grundl: questo è semplicemente una versione più estesa del dizionario D&B, che contiene anche alcuni termini presi da Grundl.

## 1) First step, import the words and create the dictionary

```{r}
# import dictionaries file
dict <-  read_excel("data/populism_dictionaries.xlsx")
variable.names(dict)

# create the dictionary
Rooduijn_Pauwels_Italian <-
  dictionary(list(populism =
                    (dict$Rooduijn_Pauwels_Italian
                     [!is.na(dict$Rooduijn_Pauwels_Italian)])))

Grundl_Italian_adapted <-
  dictionary(list(populism =
                    dict$Grundl_Italian_adapted
                  [!is.na(dict$Grundl_Italian_adapted)]))

Decadri_Boussalis <-
  dictionary(list(populism =
                    dict$Decadri_Boussalis
                  [!is.na(dict$Decadri_Boussalis)]))

Decadri_Boussalis_Grundl <-
  dictionary(list(people =
                    dict$Decadri_Boussalis_Grundl_People
                  [!is.na(dict$Decadri_Boussalis_Grundl_People)],
                  common_will =
                    dict$`Decadri_Boussalis_Grundl_Common Will`
                  [!is.na(dict$`Decadri_Boussalis_Grundl_Common Will`)],
                  elite =
                    dict$Decadri_Boussalis_Grundl_Elite
                  [!is.na(dict$Decadri_Boussalis_Grundl_Elite)]))


```

#### I also create one extra dictionary that include all the populist words

```{r}
my_dictionary <- dictionary(list(populism = c(Rooduijn_Pauwels_Italian$populism,
                                              Grundl_Italian_adapted$populism,
                                              Decadri_Boussalis$populism,
                                              Decadri_Boussalis_Grundl$people,
                                              Decadri_Boussalis_Grundl$common_will,
                                              Decadri_Boussalis_Grundl$elite)))
head(my_dictionary$populism)
tail(my_dictionary$populism)
```

## 2) Import the DFM prepared in previous steps and apply dictionaries

```{r, include=FALSE}
load("data/dfm_trimmed.Rda")
```

#### Decadri_Boussalis_Grundl

```{r}
# Daily Dictionary analysis with Decadri_Boussalis_Grundl on the whole dataset
dfm_dict1  <- dfm_lookup(DFM_trimmed, dictionary = Decadri_Boussalis_Grundl)
# Group by date
dfm_by_date1 <- dfm_group(dfm_dict1, groups= date)
dfm_by_date1
# Group by week
dfm_by_week1 <- dfm_group(dfm_dict1, groups= week)
dfm_by_week1
# Group by month
dfm_by_month1 <- dfm_group(dfm_dict1, groups= month)
dfm_by_month1
```

#### Rooduijn_Pauwels_Italian

```{r}
# Daily Dictionary analysis with Rooduijn_Pauwels_Italian on the whole dataset
dfm_dict2  <- dfm_lookup(DFM_trimmed, dictionary = Rooduijn_Pauwels_Italian)
# Group by date
dfm_by_date2 <- dfm_group(dfm_dict2, groups= date)
dfm_by_date2
# Group by week
dfm_by_week2 <- dfm_group(dfm_dict2, groups= week)
dfm_by_week2
# Group by month
dfm_by_month2 <- dfm_group(dfm_dict2, groups= month)
dfm_by_month2
```

#### Grundl_Italian_adapted

```{r}
# Daily Dictionary analysis with Grundl_Italian_adapted on the whole dataset
dfm_dict3  <- dfm_lookup(DFM_trimmed, dictionary = Grundl_Italian_adapted)
# Group by date
dfm_by_date3<- dfm_group(dfm_dict3, groups= date)
dfm_by_date3
# Group by week
dfm_by_week3 <- dfm_group(dfm_dict3, groups= week)
dfm_by_week3
# Group by month
dfm_by_month3 <- dfm_group(dfm_dict3, groups= month)
dfm_by_month3
```

#### Decadri_Boussalis

```{r}
# Daily Dictionary analysis with Decadri_Boussalis on the whole dataset
dfm_dict4  <- dfm_lookup(DFM_trimmed, dictionary = Decadri_Boussalis)
# Group by date
dfm_by_date4<- dfm_group(dfm_dict4, groups= date)
dfm_by_date4
# Group by week
dfm_by_week4 <- dfm_group(dfm_dict4, groups= week)
dfm_by_week4
# Group by month
dfm_by_month4 <- dfm_group(dfm_dict4, groups= month)
dfm_by_month4
```

#### My dictionary

```{r}
# Daily Dictionary analysis with my_dictionary on the whole dataset
dfm_dict5  <- dfm_lookup(DFM_trimmed, dictionary = my_dictionary)
# Group by date
dfm_by_date5<- dfm_group(dfm_dict5, groups= date)
dfm_by_date5
# Group by week
dfm_by_week5 <- dfm_group(dfm_dict5, groups= week)
dfm_by_week5
# Group by month
dfm_by_month5 <- dfm_group(dfm_dict5, groups= month)
dfm_by_month5
```
