---
title: "Dictionary Analysis"
author: "Riccardo Ruta"
date: "5/2022"
output: 
  pdf_document:
    toc: yes
    latex_engine: xelatex
---

```{r setup2, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
source(here::here("src","00_setup.R"))
```

# Dictionary analysis

## Create the dictionary

I imported the excel file with the words for the dictionaries, excluding NA's.

```{r}
# import dictionaries file
dict <-  read_excel("data/populism_dictionaries.xlsx")
variable.names(dict)

# create the dictionary
Rooduijn_Pauwels_Italian <-
  dictionary(list(populism =
                    (dict$Rooduijn_Pauwels_Italian
                     [!is.na(dict$Rooduijn_Pauwels_Italian)])))

Grundl_Italian_adapted <-
  dictionary(list(populism =
                    dict$Grundl_Italian_adapted
                  [!is.na(dict$Grundl_Italian_adapted)]))


Decadri_Boussalis_Grundl <-
  dictionary(list(people =
                    dict$Decadri_Boussalis_Grundl_People
                  [!is.na(dict$Decadri_Boussalis_Grundl_People)],
                  common_will =
                    dict$`Decadri_Boussalis_Grundl_Common Will`
                  [!is.na(dict$`Decadri_Boussalis_Grundl_Common Will`)],
                  elite =
                    dict$Decadri_Boussalis_Grundl_Elite
                  [!is.na(dict$Decadri_Boussalis_Grundl_Elite)]))


```

```{r}
dictionaries <- c("Rooduijn_Pauwels_Italian", "Grundl_Italian_adapted"
                  ,"Decadri_Boussalis_Grundl")
n.words <- c(
  length(Rooduijn_Pauwels_Italian$populism),
  length(Grundl_Italian_adapted$populism),
  (length(Decadri_Boussalis_Grundl$people)+
     length(Decadri_Boussalis_Grundl$common_will)+
     length(Decadri_Boussalis_Grundl$elite))
            )

number_of_words <- data.frame(dictionaries,n.words)

kable(number_of_words)
```

```{r, include=FALSE}
load("data/dfm.Rda")
```

### Group and weight the dfm

```{r}
# By party & quarter
dfm_weigh_p_quart <- dfm_group(DFM, groups = interaction(party_id, quarter))%>%
  dfm_weight(scheme = "prop")
```



\newpage

**Apply the dictionaries**

## Decadri_Boussalis_Grundl


```{r, warning=FALSE}
# Dictionary analysis with Decadri_Boussalis_Grundl
# By quarter
dfm_dict1  <- dfm_lookup(dfm_weigh_p_quart, dictionary = Decadri_Boussalis_Grundl)

```


### Transform the DFM into an ordinary dataframe
```{r}
data_dict1 <- dfm_dict1 %>% 
  quanteda::convert(to = "data.frame") %>% 
  cbind(docvars(dfm_dict1))

# Add variable with general level of populism
data_dict1 <- data_dict1 %>% mutate(populism = (people + common_will + elite) * 100)
```



### Level of populism in time

```{r}
#Over time PEOPLE (quarters)
data_quarter_people <- aggregate(x = data_dict1$people,  # Specify data column
          by = list(data_dict1$quarter),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_quarter_people$perc <- data_quarter_people$x * 100

# plot the level of the "people" component in time
plot_people <- ggplot(data = data_quarter_people, aes(x = Group.1, y = perc))+
  geom_line(color = "#00AFBB", size = 2)+
  scale_x_continuous("Quarters", labels = as.character(data_quarter_people$Group.1), breaks = data_quarter_people$Group.1)+
  ylab("Percentage of populist words - people")+
  labs(title = "Populism level over quarters of the 'people' component")
plot_people

############
#Over time COMMON WILL (quarters)
data_quarter_common <- aggregate(x = data_dict1$common_will,  # Specify data column
          by = list(data_dict1$quarter),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_quarter_common$perc <- data_quarter_common$x * 100

# plot the level of the "common will" component in time
plot_common <- ggplot(data = data_quarter_common, aes(x = Group.1, y = perc))+
  geom_line(color = "#00AFBB", size = 2)+
  scale_x_continuous("Quarters", labels = as.character(data_quarter_common$Group.1), breaks = data_quarter_common$Group.1)+
  ylab("Percentage of populist words - common will")+
  labs(title = "Populism level over quarters of the 'common will' component")
plot_common
############
#Over time ELITE (quarters)
data_quarter_elite <- aggregate(x = data_dict1$elite,  # Specify data column
          by = list(data_dict1$quarter),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_quarter_elite$perc <- data_quarter_elite$x * 100

# plot the level of the "ELITE" component in time
plot_elite <- ggplot(data = data_quarter_elite, aes(x = Group.1, y = perc))+
  geom_line(color = "#00AFBB", size = 2)+
  scale_x_continuous("Quarters", labels = as.character(data_quarter_elite$Group.1), breaks = data_quarter_elite$Group.1)+
  ylab("Percentage of populist words - elite")+
  labs(title = "Populism level over quarters of the 'elite' component")
plot_elite

#########
# compare the levels
p <- ggplot() +
  # plot people
  geom_line(data = data_quarter_people, aes(x = Group.1, y = perc, color = "people"), size = 2) +
  # plot common will
  geom_line(data = data_quarter_common, aes(x = Group.1, y = perc, color = "common will"), size = 2) +
  # plot elite
  geom_line(data = data_quarter_elite, aes(x = Group.1, y = perc, color = "elite"), size = 2) +
  scale_color_manual(name='Legend',
                     breaks=c('people', 'elite', 'common will'),
                     values=c('people'='red', 'elite'='blue', 'common will'='green'))+ 
  
  scale_x_continuous("Quarters", labels = as.character(data_quarter_people$Group.1), breaks = data_quarter_people$Group.1)+
  ylab("Percentage of populist words")+
  labs(title = " Compare the 3 components of the populism level")

p

################
#Over time general level populism (quarters)
data_quarter_general <- aggregate(x = data_dict1$populism,  # Specify data column
          by = list(data_dict1$quarter),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_quarter_general$perc <- data_quarter_general$x

# plot the level of populism
plot_general <- ggplot(data = data_quarter_general, aes(x = Group.1, y = perc))+
  geom_line(color = "#00AFBB", size = 2)+
  scale_x_continuous("Quarters", labels = as.character(data_quarter_general$Group.1), breaks = data_quarter_general$Group.1)+
  ylab("Percentage of populist words")+
  labs(title = "General level of populism over quarters")
plot_general

```

### Frequencies of the 3 components of populism for each parliamentary group
```{r, echo=FALSE}

tstat1 <- textstat_frequency(dfm_dict1, groups = party_id)

ggplot(data = tstat1, aes(x = factor(nrow(tstat1):1), y = frequency *100)) +
    geom_point() +
    facet_wrap(~ group, scales = "free") +
    coord_flip() +
    scale_x_discrete(breaks = nrow(tstat1):1,
                       labels = tstat1$feature) +
    labs(x = NULL, y = "Relative frequency")
```



### Ranking of parliamentary groups according to their level of populism

```{r}
#By party no time (quarters)

# POPULISM
data_party <- aggregate(x = data_dict1$populism,  # Specify data column
          by = list(data_dict1$party_id),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_party$perc <- round(data_party$x,3)
kable(data_party %>% select(Group.1, perc) %>%  arrange(desc(perc)))

ggplot(data=data_party, aes(x=Group.1, y=perc)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=perc), vjust=1.6, color="white", size=3.5)+
  theme_minimal()+
  geom_jitter(width=0.15)+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  ylab("Percentage of populist words") +
  xlab("Parliamentary groups")+
  labs(title = "LEVEL OF POPULISM")

# PEOPLE
data_party_people <- aggregate(x = data_dict1$people,  # Specify data column
          by = list(data_dict1$party_id),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_party_people$perc <- round(data_party_people$x * 100,3)
kable(data_party_people %>% select(Group.1, perc)%>% arrange(desc(perc)))

ggplot(data=data_party_people, aes(x=Group.1, y=perc)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=perc), vjust=1.6, color="white", size=3.5)+
  theme_minimal()+
  geom_jitter(width=0.15)+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  ylab("Percentage of populist words - people")+
  xlab("Parliamentary groups")+
  labs(title = "LEVEL OF POPULISM: PEOPLE COMPONENT")

# COMMON WILL
data_party_common <- aggregate(x = data_dict1$common_will,  # Specify data column
          by = list(data_dict1$party_id),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_party_common$perc <- round(data_party_common$x * 100,3)
kable(data_party_common %>% select(Group.1, perc)%>% arrange(desc(perc)))

ggplot(data=data_party_common, aes(x=Group.1, y=perc)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=perc), vjust=1.6, color="white", size=3.5)+
  theme_minimal()+
  geom_jitter(width=0.15)+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  ylab("Percentage of populist words - common will")+
  xlab("Parliamentary groups")+
  labs(title = "LEVEL OF POPULISM: COMMON WILL COMPONENT")

# ELITE
data_party_elite <- aggregate(x = data_dict1$elite,  # Specify data column
          by = list(data_dict1$party_id),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_party_elite$perc <- round(data_party_elite$x * 100,3)
kable(data_party_elite %>% select(Group.1, perc)%>% arrange(desc(perc)))

ggplot(data=data_party_elite, aes(x=Group.1, y=perc)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=perc), vjust=1.6, color="white", size=3.5)+
  theme_minimal()+
  geom_jitter(width=0.15)+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  ylab("Percentage of populist words - elite")+
  xlab("Parliamentary groups")+
  labs(title = "LEVEL OF POPULISM: ELITE COMPONENT")
```
Are the average values of populism for each party statistically different from each other?
The reference category is PD

```{r}
# bivariate regression for check t-test 
data_dict1$factor_party <- as.factor(data_dict1$party_id)
data_dict1$factor_party <- relevel(data_dict1$factor_party, ref = "PD")

data_dict1$factor_quarter <- as.factor(data_dict1$quarter)
data_dict1$factor_quarter <- relevel(data_dict1$factor_quarter, ref = "8")

a3 <- lm(populism ~  factor_quarter + factor_party, data_dict1 )

summary(a3)
```


### Trends in the level of populism for each parliamentary group over time

```{r}
#By party & time (quarters)
parties_time <- data_dict1 %>% select(populism, party_id, quarter)

right_party <- data_dict1 %>% select(populism, party_id, quarter) %>%
  filter(party_id == "FDI"|party_id =="FI"|party_id =="LEGA")
left_party <- data_dict1 %>% select(populism, party_id, quarter) %>%
  filter(party_id == "LEU"|party_id =="M5S"|party_id =="PD"|party_id =="IV")

# Left parties in time
ggplot(left_party, aes(x=quarter, y=populism, color=party_id)) +
  geom_line(size=1.5)+
  scale_x_continuous("Quarters", labels = as.character(left_party$quarter), breaks = left_party$quarter)+
  ylab("Percentage of populist words")+
  ggtitle("Level of populism over time for left-wing parties")

# Right parties in time
ggplot(right_party, aes(x=quarter, y=populism, color=party_id)) +
  geom_line(size=1.5)+
  scale_x_continuous("Quarters", labels = as.character(right_party$quarter), breaks = right_party$quarter)+
  ylab("Percentage of populist words")+
  ggtitle("Level of populism over time for right-wing parties")
```

```{r, eval=FALSE, include=FALSE}
# save data_dict1 for next uses
#save(data_dict1, file = "data/data_dict1.Rda")
```



\newpage


## Rooduijn_Pauwels_Italian


```{r, warning=FALSE}
# Dictionary analysis with Rooduijn_Pauwels_Italian
# By quarter
dfm_dict2  <- dfm_lookup(dfm_weigh_p_quart, dictionary = Rooduijn_Pauwels_Italian)

```

```{r}
data_dict2 <- dfm_dict2 %>% 
  quanteda::convert(to = "data.frame") %>% 
  cbind(docvars(dfm_dict2))

# Add variable with general level of populism
#data_dict2 <- data_dict2 %>% mutate(populism = (people + common_will + elite) * 100)

```


### Level of populism over time

```{r}
#Over time general level populism (quarters)
data_quarter_general2 <- aggregate(x = data_dict2$populism,  # Specify data column
          by = list(data_dict2$quarter),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_quarter_general2$perc <- data_quarter_general2$x * 100

# plot the level of populism
plot_general2 <- ggplot(data = data_quarter_general2, aes(x = Group.1, y = perc))+
  geom_line(color = "#00AFBB", size = 2)+
  scale_x_continuous("Quarters", labels = as.character(data_quarter_general2$Group.1), breaks = data_quarter_general2$Group.1)+
  ylab("Percentage of populist words")+
  labs(title = "General level of populism over quarters")
plot_general2
```

### Ranking of parliamentary groups according their populism level

```{r}

# POPULISM
data_party2 <- aggregate(x = data_dict2$populism,  # Specify data column
          by = list(data_dict2$party_id),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_party2$perc <- round(data_party2$x * 100 ,3)
kable(data_party2 %>% select(Group.1, perc) %>%  arrange(desc(perc)))

ggplot(data=data_party2, aes(x=Group.1, y=perc)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=perc), vjust=1.6, color="white", size=3.5)+
  theme_minimal()+
  ylab("Percentage of populist words")+
  xlab("Parliamentary groups")+
  labs(title = "LEVEL OF POPULISM")
```


\newpage

## Grundl_Italian_adapted



```{r, warning=FALSE}
# Dictionary analysis with Rooduijn_Pauwels_Italian
# By quarter
dfm_dict3  <- dfm_lookup(dfm_weigh_p_quart, dictionary = Grundl_Italian_adapted)

```

```{r}
data_dict3 <- dfm_dict3 %>% 
  quanteda::convert(to = "data.frame") %>% 
  cbind(docvars(dfm_dict3))

# Add variable with general level of populism
#data_dict2 <- data_dict2 %>% mutate(populism = (people + common_will + elite) * 100)

```


### Level of populism in time

```{r}
#Over time general level populism (quarters)
data_quarter_general3 <- aggregate(x = data_dict3$populism,  # Specify data column
          by = list(data_dict3$quarter),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_quarter_general3$perc <- data_quarter_general3$x * 100

# plot the level of populism
plot_general3 <- ggplot(data = data_quarter_general3, aes(x = Group.1, y = perc))+
  geom_line(color = "#00AFBB", size = 2)+
  scale_x_continuous("Quarters", labels = as.character(data_quarter_general3$Group.1), breaks = data_quarter_general3$Group.1)+
  ylab("Percentage of populist words")+
  labs(title = "General level of populism over quarters")
plot_general3
```

### Most populist parliamentary group

```{r}

# POPULISM
data_party3 <- aggregate(x = data_dict3$populism,  # Specify data column
          by = list(data_dict3$party_id),  # Specify group indicator
          FUN = mean) # Specify function (i.e. mean)
data_party3$perc <- round(data_party3$x * 100 ,3)
kable(data_party3 %>% select(Group.1, perc) %>%  arrange(desc(perc)))

ggplot(data=data_party3, aes(x=Group.1, y=perc)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=perc), vjust=1.6, color="white", size=3.5)+
  theme_minimal()+
  ylab("Percentage of populist words")+
  xlab("Parliamentary groups")+
  labs(title = "LEVEL OF POPULISM")
```






## Compare the general level of populism over time for the dictionaries

```{r, echo=FALSE, warning=FALSE}
comparison_time <- plot(data_quarter_general3$Group.1, data_quarter_general3$perc,
                        type = "l", ylab = "Populism level", xlab = "Quarters", col = "green", ylim = c(0.1,1))+
  lines(data_quarter_general2$Group.1, data_quarter_general2$perc,
        type = "l", ylab = "Populism level", xlab = "Time", col = "blue")+
  lines(data_quarter_general$Group.1, data_quarter_general$perc,
        type = "l", ylab = "Populism level", xlab = "Time", col = "red")
legend("topleft", legend = c("Groundl","Rooduijn_Pauwels",
                             "Decadri_Boussalis_Grundl"),
       fill = c("Green", "blue", "red"))
grid()
title(main = "Compare how the different dictionaries score")
```


## DA SISTEMARE LA COMPARAZIONE TRA DIZIONARI !
## Compare how the dictionaries score for the most populist parliamentary group

```{r, eval=FALSE}
# Create the columns with the "populist score"
# 11 for the "most populist" and 1 for the least
dfm_dict1_tstat_party_filtered$my_rank <- rank(dfm_dict1_tstat_party_filtered$populism)
dfm_dict2_tstat_party$my_rank <- rank(dfm_dict2_tstat_party$frequency)
dict_3_tstat_party$my_rank <- rank(dict_3_tstat_party$frequency)
dict_4_tstat_party$my_rank <- rank(dict_4_tstat_party$frequency)

# define the parliamentary group list
party <- c("LEGA","PD","M5S","FI","FDI","MISTO",
           "LEU","CI","IV","INDIPENDENTE","REG_LEAGUES")
# create an empty df
party_rank <- data.frame(first = vector(), second = vector(),
                         third = vector(), fourth = vector(), fifth = vector() )

# loop the rank for each parliamentary group
for (i in party)
{
  rank_dict_1 <- (dfm_dict1_tstat_party_filtered %>% filter(group == i ) %>% .$my_rank)
  rank_dict_2 <- (dfm_dict2_tstat_party %>% filter(group == i ) %>% .$my_rank)
  rank_dict_3 <- (dict_3_tstat_party %>% filter(group == i ) %>% .$my_rank)
  rank_dict_4 <- (dict_4_tstat_party %>% filter(group == i ) %>% .$my_rank)
  
  party <- (i)
  party_rank <- rbind(party_rank, cbind(party, rank_dict_1, rank_dict_2,
                                        rank_dict_3, rank_dict_4))
}

# change the format of the columns in numeric
party_rank$rank_dict_1 <- as.numeric(party_rank$rank_dict_1)
party_rank$rank_dict_2 <- as.numeric(party_rank$rank_dict_2)
party_rank$rank_dict_3 <- as.numeric(party_rank$rank_dict_3)
party_rank$rank_dict_4 <- as.numeric(party_rank$rank_dict_4)

# Create the column with the sum of the single score
party_rank$total_score <- rowSums(party_rank[,-1])
kable(party_rank %>% arrange(desc(total_score)), col.names = c("Party",
                                                               "Dec_Bous_Grun",
                                                               "Rood_Pau_it",
                                                               "Grun_it",
                                                               "Dec_Bous",
                                                               "Total"))
```




























