---
title: "Sentiment Analysis"
subtitle: "Analysis performed using Syuzhet Packages (www.rdocumentation.org/packages/syuzhet/versions/1.0.6)"
author: "Riccardo Ruta"
date: "5/2022"
output: 
  pdf_document:
    toc: yes
    latex_engine: xelatex
---

```{r setup3, include=FALSE}
 knitr::opts_chunk$set(echo = FALSE)
source(here::here("src","00_setup.R"))
```

```{r, include=FALSE}
# load("data/dfm_trimmed.Rda")
load("data/dataset.Rda")
```

# Sentiment analysis
<http://saifmohammad.com/WebPages/lexicons.html>

### get_nrc_sentiment
The get_nrc_sentiment implements Saif Mohammad’s NRC Emotion lexicon. According to Mohammad, “the NRC emotion lexicon is a list of words and their associations with eight emotions (anger, fear, anticipation, trust, surprise, sadness, joy, and disgust) and two sentiments (negative and positive)” (See http://saifmohammad.com/WebPages/NRC-Emotion-Lexicon.htm). The get_nrc_sentiment function returns a data frame in which each row represents a sentence from the original file. The columns include one for each emotion type was well as the positive or negative sentiment valence

## Inspect the dictionary

```{r, echo=TRUE}
# kable(head(get_sentiment_dictionary(dictionary = "nrc", language = "italian"),15))
```

### Clean text from dataframe 
Define function to make the text extracted from dataframe suitable for analysis

```{r, echo=TRUE}
# Define function to make the text suitable for analysis
clean.text = function(x)
{
  # tolower
  x = tolower(x)
  # remove rt
  x = gsub("rt", "", x)
  # remove at
  x = gsub("@\\w+", "", x)
  # remove punctuation
  x = gsub("[[:punct:]]", "", x)
  # remove numbers
  x = gsub("[[:digit:]]", "", x)
  # remove links http
  x = gsub("http\\w+", "", x)
  # remove tabs
  x = gsub("[ |\t]{2,}", "", x)
  # remove blank spaces at the beginning
  x = gsub("^ ", "", x)
  # remove blank spaces at the end
  x = gsub(" $", "", x)
  return(x)
}
```

## Clean the dataset

```{r, eval=FALSE}
# Call the function previously defined and remove stopwords
system.time(
  dataset_cleaned <- clean.text(dataset))
system.time(  
  dataset_cleaned <-  removeWords(dataset_cleaned,  c(stopwords("italian"))))
save(dataset_cleaned,file="data/dataset_cleaned.Rda")
     ```


## Create the filtered dataframes

```{r, echo=TRUE}
# Create filtered dataframes
#MELONI <- dataset %>% filter(nome  == "MELONI Giorgia")
#CONTE <- dataset %>% filter(nome  == "CONTE Giuseppe")
#RENZI <- dataset %>% filter(nome  == "RENZI Matteo")
#SALVINI <- dataset %>% filter(nome  == "SALVINI Matteo")
#LETTA <- dataset %>% filter(nome  == "LETTA Enrico")
#BERLUSCONI <- dataset %>% filter(nome  == "BERLUSCONI Silvio")
#SPERANZA <- dataset %>% filter(nome  == "SPERANZA Roberto")

PD <- dataset_cleaned %>% filter(party_id == "PD")
FDI <- dataset_cleaned %>% filter(party_id == "FDI")
M5S <- dataset_cleaned %>% filter(party_id == "M5S")
FI <- dataset_cleaned %>% filter(party_id == "FI")
REG_LEAGUES <- dataset_cleaned %>% filter(party_id == "REG_LEAGUES")
MISTO <- dataset_cleaned %>% filter(party_id == "MISTO")
LEGA <- dataset_cleaned %>% filter(party_id == "LEGA")
IV <- dataset_cleaned %>% filter(party_id == "IV")
INDIPENDENTE <- dataset_cleaned %>% filter(party_id == "INDIPENDENTE")
CI <- dataset_cleaned %>% filter(party_id == "CI")
LEU <- dataset_cleaned %>% filter(party_id == "LEU")

```

## Create nrc objects
```{r, eval=F, echo=TRUE}
# Create the nrc object
#nrc_meloni <- get_nrc_sentiment(MELONI$tweet_testo, language="italian")
#save(nrc_meloni,file="data/nrc_meloni.Rda")

#nrc_conte <- get_nrc_sentiment(CONTE$tweet_testo, language="italian")
#save(nrc_conte,file="data/nrc_conte.Rda")

#nrc_renzi <- get_nrc_sentiment(RENZI$tweet_testo, language="italian")
#save(nrc_renzi,file="data/nrc_renzi.Rda")

#nrc_salvini <- get_nrc_sentiment(SALVINI$tweet_testo, language="italian")
#save(nrc_salvini,file="data/nrc_salvini.Rda")

#nrc_letta <- get_nrc_sentiment(LETTA$tweet_testo, language="italian")
#save(nrc_letta,file="data/nrc_letta.Rda")

#nrc_berlusconi <- get_nrc_sentiment(BERLUSCONI$tweet_testo, language="italian")
#save(nrc_berlusconi, file="data/nrc_berlusconi.Rda")

#nrc_speranza <- get_nrc_sentiment(SPERANZA$tweet_testo, language="italian")
#save(nrc_speranza,file="data/nrc_speranza.Rda")

################
 system.time(
nrc_PD <- get_nrc_sentiment(PD$tweet_testo, language="italian")
save(nrc_PD,file="data/nrc_PD.Rda")

nrc_FDI <- get_nrc_sentiment(FDI$tweet_testo, language="italian")
save(nrc_FDI,file="data/nrc_FDI.Rda")

nrc_M5S <- get_nrc_sentiment(M5S$tweet_testo, language="italian")
save(nrc_M5S,file="data/nrc_M5S.Rda")

nrc_FI <- get_nrc_sentiment(FI$tweet_testo, language="italian")
save(nrc_FI,file="data/nrc_FI.Rda")

nrc_REG_LEAGUES <- get_nrc_sentiment(REG_LEAGUES$tweet_testo, language="italian")
save(nrc_REG_LEAGUES,file="data/nrc_REG_LEAGUES.Rda")

nrc_MISTO <- get_nrc_sentiment(MISTO$tweet_testo, language="italian")
save(nrc_MISTO,file="data/nrc_MISTO.Rda")

nrc_LEGA <- get_nrc_sentiment(LEGA$tweet_testo, language="italian")
save(nrc_LEGA,file="data/nrc_LEGA.Rda")

nrc_IV <- get_nrc_sentiment(IV$tweet_testo, language="italian")
save(nrc_IV,file="data/nrc_IV.Rda")

nrc_INDIPENDENTE <- get_nrc_sentiment(INDIPENDENTE$tweet_testo, language="italian")
save(nrc_INDIPENDENTE,file="data/nrc_INDIPENDENTE.Rda")

nrc_CI <- get_nrc_sentiment(CI$tweet_testo, language="italian")
save(nrc_CI,file="data/nrc_CI.Rda")

nrc_LEU <- get_nrc_sentiment(LEU$tweet_testo, language="italian")
save(nrc_LEU,file="data/nrc_LEU.Rda")
)

```

```{r, include=FALSE}
# load nrc object
#load("data/nrc_meloni.Rda")
#load("data/nrc_conte.Rda")
#load("data/nrc_renzi.Rda")
#load("data/nrc_salvini.Rda")
#load("data/nrc_letta.Rda")
#load("data/nrc_berlusconi.Rda")
#load("data/nrc_speranza.Rda")

load("data/nrc_PD.Rda")
load("data/nrc_FDI.Rda")
load("data/nrc_M5S.Rda")
load("data/nrc_FI.Rda")
load("data/nrc_REG_LEAGUES.Rda")
load("data/nrc_MISTO.Rda")
load("data/nrc_LEGA.Rda")
load("data/nrc_IV.Rda")
load("data/nrc_INDIPENDETE.Rda")
load("data/nrc_CI.Rda")
load("data/nrc_LEU.Rda")
```

\newpage

## Partito Democratico
### Proportion of the emotion

```{r,echo=TRUE}
barplot(
  sort(colSums(prop.table(nrc_PD[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Partito Democratico ", xlab="Percentage"
)
```

### Wordcloud of emotions

```{r, warning=FALSE, echo=TRUE}
all <- c(
  paste(PD$tweet_testo[nrc_PD$anger > 0], collapse=" "),
  paste(PD$tweet_testo[nrc_PD$anticipation > 0], collapse=" "),
  paste(PD$tweet_testo[nrc_PD$disgust > 0], collapse=" "),
  paste(PD$tweet_testo[nrc_PD$fear > 0], collapse=" "),
  paste(PD$tweet_testo[nrc_PD$joy > 0], collapse=" "),
  paste(PD$tweet_testo[nrc_PD$sadness > 0], collapse=" "),
  paste(PD$tweet_testo[nrc_PD$surprise > 0], collapse=" "),
  paste(PD$tweet_testo[nrc_PD$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear',
                   'joy', 'sadness', 'surprise', 'trust')
# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Partito Democratico')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099",
                            "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage


## Fratelli d'Italia
### Proportion of the emotion
```{r}
barplot(
  sort(colSums(prop.table(nrc_FDI[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Fratelli d'Italia", xlab="Percentage"
)
```

### Wordcloud of emotions

```{r, warning=FALSE, echo=FALSE}
all <- c(
  paste(FDI$tweet_testo[nrc_FDI$anger > 0], collapse=" "),
  paste(FDI$tweet_testo[nrc_FDI$anticipation > 0], collapse=" "),
  paste(FDI$tweet_testo[nrc_FDI$disgust > 0], collapse=" "),
  paste(FDI$tweet_testo[nrc_FDI$fear > 0], collapse=" "),
  paste(FDI$tweet_testo[nrc_FDI$joy > 0], collapse=" "),
  paste(FDI$tweet_testo[nrc_FDI$sadness > 0], collapse=" "),
  paste(FDI$tweet_testo[nrc_FDI$surprise > 0], collapse=" "),
  paste(FDI$tweet_testo[nrc_FDI$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear', 'joy',
                   'sadness', 'surprise', 'trust')
# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, "Emotion Comparison Word Cloud for tweets by Fratelli d'Italia")
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099",
                            "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage

## Movimento 5 Stelle
### Proportion of the emotion

```{r}
barplot(
  sort(colSums(prop.table(nrc_M5S[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Movimento 5 Stelle", xlab="Percentage"
)
```

### Wordcloud of emotions

```{r, warning=FALSE, echo=FALSE}
all <- c(
  paste(M5S$tweet_testo[nrc_M5S$anger > 0], collapse=" "),
  paste(M5S$tweet_testo[nrc_M5S$anticipation > 0], collapse=" "),
  paste(M5S$tweet_testo[nrc_M5S$disgust > 0], collapse=" "),
  paste(M5S$tweet_testo[nrc_M5S$fear > 0], collapse=" "),
  paste(M5S$tweet_testo[nrc_M5S$joy > 0], collapse=" "),
  paste(M5S$tweet_testo[nrc_M5S$sadness > 0], collapse=" "),
  paste(M5S$tweet_testo[nrc_M5S$surprise > 0], collapse=" "),
  paste(M5S$tweet_testo[nrc_M5S$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear',
                   'joy', 'sadness', 'surprise', 'trust')
# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Movimento 5 Stelle')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099",
                            "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage

## Forza Italia

### Proportion of the emotion

```{r}
barplot(
  sort(colSums(prop.table(nrc_FI[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Forza Italia", xlab="Percentage"
)
```

### Wordcloud of emotions

```{r, warning=FALSE}
all <- c(
  paste(FI$tweet_testo[nrc_FI$anger > 0], collapse=" "),
  paste(FI$tweet_testo[nrc_FI$anticipation > 0], collapse=" "),
  paste(FI$tweet_testo[nrc_FI$disgust > 0], collapse=" "),
  paste(FI$tweet_testo[nrc_FI$fear > 0], collapse=" "),
  paste(FI$tweet_testo[nrc_FI$joy > 0], collapse=" "),
  paste(FI$tweet_testo[nrc_FI$sadness > 0], collapse=" "),
  paste(FI$tweet_testo[nrc_FI$surprise > 0], collapse=" "),
  paste(FI$tweet_testo[nrc_FI$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear',
                   'joy', 'sadness', 'surprise', 'trust')
# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Forza Italia')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099",
                            "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage

## Regional Leagues

### Proportion of the emotion
```{r}
barplot(
  sort(colSums(prop.table(nrc_REG_LEAGUES[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Regional Leagues", xlab="Percentage"
)
```

### Wordcloud of emotions
```{r, warning=FALSE}
all <- c(
  paste(REG_LEAGUES$tweet_testo[nrc_REG_LEAGUES$anger > 0], collapse=" "),
  paste(REG_LEAGUES$tweet_testo[nrc_REG_LEAGUES$anticipation > 0], collapse=" "),
  paste(REG_LEAGUES$tweet_testo[nrc_REG_LEAGUES$disgust > 0], collapse=" "),
  paste(REG_LEAGUES$tweet_testo[nrc_REG_LEAGUES$fear > 0], collapse=" "),
  paste(REG_LEAGUES$tweet_testo[nrc_REG_LEAGUES$joy > 0], collapse=" "),
  paste(REG_LEAGUES$tweet_testo[nrc_REG_LEAGUES$sadness > 0], collapse=" "),
  paste(REG_LEAGUES$tweet_testo[nrc_REG_LEAGUES$surprise > 0], collapse=" "),
  paste(REG_LEAGUES$tweet_testo[nrc_REG_LEAGUES$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear', 'joy', 'sadness', 'surprise', 'trust')
# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Regional Leagues')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099", "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage

## Gruppo Misto

### Proportion of the emotion
```{r}
barplot(
  sort(colSums(prop.table(nrc_MISTO[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Gruppo Misto", xlab="Percentage"
)
```

### Wordcloud of emotions
```{r, warning=FALSE}
all <- c(
  paste(MISTO$tweet_testo[nrc_MISTO$anger > 0], collapse=" "),
  paste(MISTO$tweet_testo[nrc_MISTO$anticipation > 0], collapse=" "),
  paste(MISTO$tweet_testo[nrc_MISTO$disgust > 0], collapse=" "),
  paste(MISTO$tweet_testo[nrc_MISTO$fear > 0], collapse=" "),
  paste(MISTO$tweet_testo[nrc_MISTO$joy > 0], collapse=" "),
  paste(MISTO$tweet_testo[nrc_MISTO$sadness > 0], collapse=" "),
  paste(MISTO$tweet_testo[nrc_MISTO$surprise > 0], collapse=" "),
  paste(MISTO$tweet_testo[nrc_MISTO$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear',
                   'joy', 'sadness', 'surprise', 'trust')
# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Gruppo Misto')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099",
                            "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage

## Lega Salvini

### Proportion of the emotion
```{r}
barplot(
  sort(colSums(prop.table(nrc_LEGA[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Lega", xlab="Percentage"
)
```

### Wordcloud of emotions
```{r, warning=FALSE}
all <- c(
  paste(LEGA$tweet_testo[nrc_LEGA$anger > 0], collapse=" "),
  paste(LEGA$tweet_testo[nrc_LEGA$anticipation > 0], collapse=" "),
  paste(LEGA$tweet_testo[nrc_LEGA$disgust > 0], collapse=" "),
  paste(LEGA$tweet_testo[nrc_LEGA$fear > 0], collapse=" "),
  paste(LEGA$tweet_testo[nrc_LEGA$joy > 0], collapse=" "),
  paste(LEGA$tweet_testo[nrc_LEGA$sadness > 0], collapse=" "),
  paste(LEGA$tweet_testo[nrc_LEGA$surprise > 0], collapse=" "),
  paste(LEGA$tweet_testo[nrc_LEGA$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear', 'joy', 'sadness', 'surprise', 'trust')

# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Lega Salvini')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099", "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage

## Italia Viva

### Proportion of the emotion
```{r}
barplot(
  sort(colSums(prop.table(nrc_IV[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Italia Viva", xlab="Percentage"
)
```

### Wordcloud of emotions
```{r, warning=FALSE}
all <- c(
  paste(IV$tweet_testo[nrc_IV$anger > 0], collapse=" "),
  paste(IV$tweet_testo[nrc_IV$anticipation > 0], collapse=" "),
  paste(IV$tweet_testo[nrc_IV$disgust > 0], collapse=" "),
  paste(IV$tweet_testo[nrc_IV$fear > 0], collapse=" "),
  paste(IV$tweet_testo[nrc_IV$joy > 0], collapse=" "),
  paste(IV$tweet_testo[nrc_IV$sadness > 0], collapse=" "),
  paste(IV$tweet_testo[nrc_IV$surprise > 0], collapse=" "),
  paste(IV$tweet_testo[nrc_IV$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear', 'joy', 'sadness', 'surprise', 'trust')

# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Italia Viva')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099", "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage

## Gruppo Indipendente

### Proportion of the emotion
```{r}
barplot(
  sort(colSums(prop.table(nrc_INDIPENDETE[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Gruppo Indipendente", xlab="Percentage"
)
```

### Wordcloud of emotions
```{r, warning=FALSE}
all <- c(
  paste(INDIPENDENTE$tweet_testo[nrc_INDIPENDETE$anger > 0], collapse=" "),
  paste(INDIPENDENTE$tweet_testo[nrc_INDIPENDETE$anticipation > 0], collapse=" "),
  paste(INDIPENDENTE$tweet_testo[nrc_INDIPENDETE$disgust > 0], collapse=" "),
  paste(INDIPENDENTE$tweet_testo[nrc_INDIPENDETE$fear > 0], collapse=" "),
  paste(INDIPENDENTE$tweet_testo[nrc_INDIPENDETE$joy > 0], collapse=" "),
  paste(INDIPENDENTE$tweet_testo[nrc_INDIPENDETE$sadness > 0], collapse=" "),
  paste(INDIPENDENTE$tweet_testo[nrc_INDIPENDETE$surprise > 0], collapse=" "),
  paste(INDIPENDENTE$tweet_testo[nrc_INDIPENDETE$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear', 'joy', 'sadness', 'surprise', 'trust')

# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Gruppo Indipendente')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099", "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage

## Coraggio Italia

### Proportion of the emotion
```{r}
barplot(
  sort(colSums(prop.table(nrc_CI[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Coraggio Italia", xlab="Percentage"
)
```

### Wordcloud of emotions
```{r, warning=FALSE}
all <- c(
  paste(CI$tweet_testo[nrc_CI$anger > 0], collapse=" "),
  paste(CI$tweet_testo[nrc_CI$anticipation > 0], collapse=" "),
  paste(CI$tweet_testo[nrc_CI$disgust > 0], collapse=" "),
  paste(CI$tweet_testo[nrc_CI$fear > 0], collapse=" "),
  paste(CI$tweet_testo[nrc_CI$joy > 0], collapse=" "),
  paste(CI$tweet_testo[nrc_CI$sadness > 0], collapse=" "),
  paste(CI$tweet_testo[nrc_CI$surprise > 0], collapse=" "),
  paste(CI$tweet_testo[nrc_CI$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear', 'joy', 'sadness', 'surprise', 'trust')

# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Coraggio Italia')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099", "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```

\newpage

## Liberi e Uguali

### Proportion of the emotion
```{r}
barplot(
  sort(colSums(prop.table(nrc_LEU[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in tweets by Liberi e Uguali", xlab="Percentage"
)
```

### Wordcloud of emotions
```{r, warning=FALSE}
all <- c(
  paste(LEU$tweet_testo[nrc_LEU$anger > 0], collapse=" "),
  paste(LEU$tweet_testo[nrc_LEU$anticipation > 0], collapse=" "),
  paste(LEU$tweet_testo[nrc_LEU$disgust > 0], collapse=" "),
  paste(LEU$tweet_testo[nrc_LEU$fear > 0], collapse=" "),
  paste(LEU$tweet_testo[nrc_LEU$joy > 0], collapse=" "),
  paste(LEU$tweet_testo[nrc_LEU$sadness > 0], collapse=" "),
  paste(LEU$tweet_testo[nrc_LEU$surprise > 0], collapse=" "),
  paste(LEU$tweet_testo[nrc_LEU$trust > 0], collapse=" ")
)
# Call the function previously defined
all <- clean.text(all)
# remove stop-words
all = removeWords(all,  c(stopwords("italian")))
# create corpus
corpus_viz <- Corpus(VectorSource(all))
# create term-document matrix
tdm <- TermDocumentMatrix(corpus_viz)
# convert as matrix
tdm <- as.matrix(tdm)
# add column names
colnames(tdm) <- c('anger', 'anticipation', 'disgust', 'fear', 'joy', 'sadness', 'surprise', 'trust')

# Plot comparison wordcloud
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 'Emotion Comparison Word Cloud for tweets by Liberi e Uguali')
comparison.cloud(tdm, random.order=FALSE,
                 colors = c("#00B2FF", "red", "#FF0099", "#6600CC", "green", "orange", "blue", "brown"),
                 title.size=1.5, max.words=80)
```